### 2024-11-26 paper/paper.qmd
Updated model and data section of the paper

---
title: "Fire Safety Regulation Violations in Toronto: Analysis by Property Type and Inspection Duration for Inspections Closed in 2024"
subtitle: "My subtitle if needed"
author: 
  - Yunkai Gu
thanks: "Code and data are available at: [https://github.com/Kylie309/Toronto-Fire-Inspection](https://github.com/Kylie309/Toronto-Fire-Inspection)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

# Workspace setup
library(tidyverse)
library(janitor)
library(lubridate)
library(broom)
library(modelsummary)
library(rstanarm)
library(splines)
library(ggplot2)
library(arrow)
library(knitr)
library(RColorBrewer)

# Read the cleaned data
data <- read_csv(
  file = here::here("data/02-analysis_data/fire_cleaned_data.csv")
  )
```

# Introduction

Overview paragraph

Estimand paragraph

Results paragraph

Why it matters paragraph

Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

## Overview

This paper uses Highrise Residential Fire Inspection Results dataset obtained from Open Data Toronto as the main source of data [@fire_data]. The portal is launched by City of Toronto to meet growing demand for open data. The raw dataset presents information of properties where Inspectors from Toronto Fire Services (TFS) have examined on, as well as whether the properties violated fire safety regulations and the details of violations if so.

We use the statistical programming language R [@citeR]....

Following @tellingstories, this paper uses Bayesian modeling to predict the pass or fail status for safety checks of the properties in Toronto. The factors of region, property type and inspection time intervals from the dataset are mainly chosen and considered to examine their effects on the likelihood of violations for the properties.

## Measurement {#sec-measure}

The dataset captures data related to the results of fire safety inspections conducted by Toronto Fire Services (TFS) within highrise residential buildings, which is guided by the Fire Protection and Prevention Act, 1997 (FPPA) and regulations under the FPPA, like the Ontario Fire Code [@fire_info]. It indicates properties where violations have been found by an Inspector which are required to be fixed for compliance at the time with the Ontario Fire Code as well as properties with no observable violations [@fire_data].

The data collection process was conducted by TFS Fire Inspectors. Inspectors assess tangible aspects of fire safety based on observable and measurable attributes of the physical environment within the properties, such as proper storage of combustible materials, functionality of fire alarms and fire pumps, maintenance records for fire safety equipment and others in reference to the regulations under FPPA.

After the inspections were completed, the observations have been translated into records and written into collected data. The raw data entry presented by Open Data Toronto includes three main aspects: property identifier (such as address, property type), inspection information (such as inspection start and end dates), and inspection outcomes (pass or fail status for safety checks, and details of violations).

Note that this dataset only includes 'closed' cases, which are cases whose inspection processes have ended. The ongoing inspections were not available in the dataset, and therefore would lead to potential loss of information. This would be further evaluated in detail in the discussion section.

## Outcome Variable

### Violation

The outcome variable for the model is the violation status of the properties. In other words, it is the variable that represents whether the properties inspected have been found violating fire safety regulations by an Inspector or not.

In the raw dataset, columns 'VIOLATION_FIRE_CODE', 'VIOLATION_DESCRIPTION' and 'VIOLATIONS_ITEM_NUMBER' indicates the outcome of the inspections. The previous two provides detailed information on fire code under which violation was noted. The latter one presents the order number of violations by code, and shows 0 if no violations observed.

Therefore, a new column 'violation' is mutated to make the analysis procedure easier. It contains numeric values of 1 and 0, which indicates violation observed and no violation observed respectively. The outcome variable is thus binary.

@fig-violation presents the visualized counts of properties that were found violations versus those that were not. The height of each bar shows the total number of cases corresponding to each category. We could see that the orange bar is significantly taller, indicating that among all cases selected for analysis, violations were reported more frequently in the dataset (9829 cases out of 13193). On the other hand, the blue bar is shorter, indicating there were fewer cases without violations (3364 cases out of 13193).

In conclusion, the data contains a higher number of cases with violations (1) compared to cases where no violations were observed (0), suggesting that violations are common.

```{r}
#| label: fig-violation
#| fig-cap: Counts of Properties that Were Found Violations versus Those that Were Not
#| echo: false
#| warning: false
#| message: false

# Create bar plot
data |>
  ggplot(aes(x = as.factor(violation), fill = as.factor(violation))) +
  geom_bar(color = "black") +
  labs(
    x = "Violation Status",
    y = "Count",
    fill = "Violation Status" # Legend title
  ) +
  scale_fill_manual(
    values = c("skyblue", "orange"),
    labels = c("No Violation Observed (Denoted as 0)", "Violation Observed (Denoted as 1)")
    ) + 
  theme_minimal() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12),
    axis.text = element_text(size = 10),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10)
  )

```

## Predictor Variables

### Inspection Time Interval

One predictor included in the model is the inspection time interval. It refers to the duration of the fire inspections conducted by the TFS Inspector for each case.

In the raw dataset, there are two columns recording the date: 'INSPECTIONS_OPENDATE' and 'INSPECTIONS_CLOSEDDATE'. Previous one is the date TFS opened the inspection file, whereas the latter one is the date TFS closed inspection file or date or date enforcement proceedings ended (whichever is later).

During the data cleaning process, the date is converted into time interval to enable easier analysis. A new column named 'date_num' is mutated by calculating the time difference between the end time and the start time of the inspection, in the unit of days.

@fig-date shows the distribution of the inspection time interval. X-axis represents the number of days of each inspection case, and Y-axis represents the counts. The distribution has peak at low intervals, and the highest bar is near 0 days, indicating that a large number of properties have very short inspection time intervals. The right-skewed inspection suggests that as the inspection interval increases, the corresponding counts decrease stably. The long tail of the right-hand side of the distribution means that there are properties with very long intervals (up to 1500 days or more).

```{r}
#| label: fig-date
#| fig-cap: Distribution of Inspection Time Interval
#| echo: false
#| warning: false
#| message: false

data |> 
  ggplot(aes(x = date_num)) + 
  geom_histogram(fill = "skyblue", color = "black", alpha = 0.7) +
  labs(x = "Inspection Time Interval (Days)",
       y = "Counts of Properties") +
  theme_minimal()

```

### Property Type

The second predictor variable included in the model is the property type. It refers to the occupancy type of the property where the inspection took place, and is directly contains in the raw dataset.

To visualize the variable, two bar plots are created separately in @fig-type. The left panel presents the number of occurrences of "High Rise" and "Low Rise", with the bar representing "High Rise" relatively taller, indicating a higher count compared to low rise. This suggests that the inspection results and data collection focus more heavily on high-rise buildings.

The right panel includes the other categories of properties. Specifically, the types include: "Detention," "Group Home," "Group Home (VO)," "Hospital," "Hotel & Motel," "Nursing Home," "Residential Care," and "Rooming House." We could see that "Rooming House" has the highest count among these property types, whereas categories of "Detention" and "Group Home" have relatively lower counts, indicating that they are less represented in the dataset.

In general, there is a diverse distribution across the property types, with some being far less frequent than others. High-rise properties dominate overall, while rooming houses stand out within other categories. The dataset might reflect an emphasis on inspecting high-rise and rooming houses more than other property types.

```{r}
#| label: fig-type
#| fig-cap: Counts of Property Types
#| echo: false
#| warning: false
#| message: false
#| fig-subcap: ["High Rise versus Low Rise", "Other Types"]
#| layout-ncol: 2

data_rise <- data %>% 
  filter(property_type == "High Rise" | property_type == "Low Rise")

data_other <- data %>% 
  filter(property_type != "High Rise" & property_type != "Low Rise")

# Create bar plot for high rise properties versus low rise properties
data_rise |>
  ggplot(
    aes(x = as.factor(property_type), 
        fill = as.factor(property_type))
    ) +
  geom_bar(color = "black") +
  labs(
    x = "Property Type",
    y = "Count",
    fill = "Property Type"
  ) +
  theme_minimal() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12),
    axis.text.x = element_text(size = 10, angle = 45, hjust = 1), 
    axis.text.y = element_text(size = 10),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10)
  )

# Create bar plot for other property types
data_other |>
  ggplot(
    aes(x = as.factor(property_type), 
        fill = as.factor(property_type))
    ) +
  geom_bar(color = "black") +
  labs(
    x = "Property Type",
    y = "Count",
    fill = "Property Type" 
  ) +
  theme_minimal() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12),
    axis.text.x = element_text(size = 10, angle = 45, hjust = 1), 
    axis.text.y = element_text(size = 10),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10)
  )

```

# Model

The goal of the modelling strategy is twofold.

Firstly and most importantly, from the statistical standpoint, the goal is to estimate the the detection of violation from an inspection based on its time interval and the property type.

Secondly, from a more practical standpoint, by predicting which type of property with how long duration is more likely to be observed violations, more efficient inspection process could be constructed. Identifying certain property types that would more frequently violate the fire safety regulations could provide guidelines for interventions and help to establish targeted and focused actions towards them.

The model constructed in the paper is Bayesian logistics regression model designed to predict the violation status (denoted as violation) based on the fixed effect of inspection time interval (denoted as date_num) and property type (denoted as property_type). It is designed to predict the inspection results based on the two predictor variables.

Following sections define, explain and justify each model and the variables, as well as discuss underlying assumptions, potential limitations, software used to implement the model, and evidence of model validation and checking.

Background details and diagnostics of the model are included in [Appendix -@sec-model-details].

## Model set-up

The Bayesian model was implemented using the R programming language [@citeR], specifically utilizing the `rstanarm` package of @citerstanarm. This package provides an interface for fitting Bayesian regression models using Stan, and the models are fit using the package.

Define $y_i$ as the binary response variable for observation $i$. $y_i=1$ indicates that the case has been observed violations, while $y_i=0$ indicates that no violation occurs. It follows a Bernoulli distribution:

$$y_i=\text{Bernoulli}(p_i)$$

where $p_i$ is the probability of a property that is observed to have violations of fire safety regulations.

Then define the inspection time interval for observation $i$ as date_num and the property type as property_type.

The Bayesian model could be defined by the following mathematical expressions:

$$ \text{logit}(p_i) = \beta_0 + \beta_1 \cdot \text{date}_i + \beta_2 \cdot \text{type}_i $$
$$ \text{logit}(p_i) = \log\left(\frac{p_i}{1 - p_i}\right) $$
$$ \beta_0 \sim \mbox{Normal}(0, 2.5) $$
$$ \beta_1 \sim \mbox{Normal}(0, 2.5) $$
$$ \beta_2 \sim \mbox{Normal}(0, 2.5) $$

where:

- $\text{logit}(p_i) = \log\left(\frac{p_i}{1 - p_i}\right)$ is the log-odds of $p_i$.
- $\beta_0$ is the intercept term of the Bayesian logistic regression, representing the baseline log-odds of a violation when `date_num = 0` and `property_type` is the reference category. Formula (2) specifies that $\beta_0$ follows normal distribution with mean equals 0 and variance equals $2.5^2$.
- $\beta_1$ is the coefficient for predictor variable `date_num`, representing the change in log-odds of a violation per unit increase in `date_num`, the inspection time interval. Formula (3) specifies that $\beta_1$ follows normal distribution with mean equals 0 and variance equals $2.5^2$.
- $\beta_2$ is the coefficient for predictor variable `property_type`, representing the change in log-odds of a violation per unit increase in `property_type`. Formula (4) specifies that $\beta_2$ follows normal distribution with mean equals 0 and variance equals $2.5^2$.

Formula (2), (3) and (4) specifies priors for the model. This prior reflects the assumption that coefficients are centered around 0, with a standard deviation of 2.5, allowing moderate variability while discouraging extreme values.

## Model Assumptions and Limitations

The main, underlying assumptions and their limitations for the Bayesian model is discussed below:

Firstly, the model assumes that each observation is independent of others. This assumption suggests that violations at one property should not influence violations at another property unless explicitly modeled (e.g., through random effects).

If observations are clustered and the assumption is violated (for instance, multiple observations were conducted in the same region or by the same inspector), overestimation and underestimation of standard errors and outcomes may occur.

Secondly, the model assumes linearity in the logit. This assumption stated that the log-odds of the response variable ($\text{logit}(p_i)$) are a linear function of the predictors.

If violations change non-linearly over time, the model assumption would be violated, potentially resulting in misfit of the model.

Thirdly, the model assumes priors of $\text{Norma}(0,2.5)$ for the coefficients. They were constructed on domain knowledge, and poorly chosen priors could make the estimation outcome biased.

Also, if new property_type levels are introduced, the model may not be no longer appropriate for the new situation, as fixed effects could not be feasible to compute estimates. Random effects, then, may be more appropriate.

## Model Justification

Since the response variable is binary for each case and follows a Bernoulli distribution, it would be appropriate to use Bayesian logistic regression model to estimate it.

The predictor variable as 'date_num' is modeled as fixed effect in the model. There are various reasons for this. Firstly, As 'date_num' represents the number of days for the inspection takes place, it is a numeric variable. Modeling it as a fixed effect allows the model to estimate its direct, continuous influence on the response variable. Secondly, since it applies across all observations, regardless of property type, modeling it as a fixed effect could consider its impact consistently across the entire dataset. It also makes the coefficient of 'date_num' ($beta_1$) be easier to interpret, avoids adding complexity to the model.

The other predictor variable 'property_type' is also modeled as fixed effect. Since it is categorical variable, modeling it as fixed effect allow the model to estimate a separate coefficient for each category, relative to a reference level. This would make it easier to compare between property types, in order to understand which types of properties would be observed to have violations. Moreover, since 'property_type' has only 10 levels, it is feasible to compute it as fixed effect and conduct estimation without overloading the model.

The prior of $Normal(0,2.5)$ for every coefficients is also reasonable because it reflects prior knowledge that most predictors have small-to-moderate effects on the log-odds scale. This assumption would avoid overfitting to extreme values.

The above final model decision is made after considering several alternative models and variants. One alternative is a simple linear regression model (SLR), which assumes a constant linear relationship between the predictor (violation) and the response (date_num). Although the model is extremely straightforward and easy to interpret, it is far too simple for estimating and neglect the key variable of 'property_type'. More importantly, the response variable is binary, whereas SLR assumes a continuous response variable. MLR also assumes so, and therefore is considered and rejected because of the same reason.

Another alternative considered is the Bayesian model with natural splines (e.g. $f(\text{date}_i)$). While it could model complex, non-linear time trends and is appropriate for 'date_num', the expected model for this study does not primarily focus on exploratory analysis on non-linear relationships between date_num and violations. Non-linear functions would also overfit the data if not regularized properly.

While considering alternative Bayesian logistics model, the model with 'property_type' as fixed effect was also considered. This would capture variability across property types without explicitly estimating coefficients for each type, and does not provide explicit estimates for each property type. The model would be suitable if there are many property types, but the number of types is manageable to include it in the model as fixed effect.

Therefore, after considering many alternatives, the final model of Bayesian logistics model with 'date_num' and 'property_type' as fixed effect is chosen. It could directly provides explicit comparisons between property types without overfitting the model, and meet the focus of the research question.

# Results

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

model <-
  readRDS(file = here::here("models/model_1.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  models = model,
  statistic = "mad",
  fmt = 2
)

#modelsummary::modelsummary(
#  list(
#    "First model" = model,
#  ),
#  statistic = "mad",
#  fmt = 2
#)
```

# Discussion

## What is done in this paper?

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## What is something that we learn about the world?

Please don't use these as sub-heading labels - change them to be what your point actually is.

## What is another thing that we learn about the world?

## Weaknesses and next steps

Firstly, the limitations in the process of measurement of the original dataset should be considered. Specifically, the limitations include:

- Observer Bias

Although inspectors conduct the violation detection procedure in reference to the same, standardized fire safety regulations (Ontario Fire Code, FPPA and Municipal Code, according to City of Toronto) to ensure consistency, their subjective judgment could still play a significant role in the examination process.

Various interpretations of the guidelines and different decision-making procedures made by the inspectors based on specific situations could impact the outcome of the inspection. Since the examinations have been thoroughly completed by human, the assessments could differ depending on the inspectors' focus and perspectives on certain regulations, influencing the observations recorded, even with clear rules.

- Data Completeness

The dataset does not capture all fire safety-related phenomena in Toronto, as it only contains the properties that have been inspected by the Inspectors from TFS. The properties that are not included in the list fail to provide any information, which would make the dataset not representative enough to conclude the situations of fire safety checks for the whole city.

Moreover, even for the properties that have been inspected by TFS, not all cases are recorded in the dataset. The raw dataset only includes 'closed' cases, which are specific cases where the inspection process has ended, and does not account for cases currently under review or in progress.

In other words, the properties whose initial observations have been made but further investigation or corrective actions are required, are excluded from the dataset. Therefore, the dataset does not represent the full scope of fire safety checks at any given time. The active cases would be neglected in analysis procedure, providing limited insights to identify fire safety concerns in real-time.

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior Predictive Check

During the modeling process, posterior predictive checks (PPC) is used.

PPC is the comparison between what the fitted model predicts and the actual observed data, which validates whether the fitted model is compatible with the observed data. The aim is to detect if the model is inadequate to describe the data [@ppcheck]. This type of diagnostic visualizes the fit of the model by comparing the observed data ($y$) to the posterior predictive distributions ($y_{rep}$) generated by the model.

In this PPC plot, x-axis represents predicted probability of the binary outcome $p_i$, which is the probability of observing violation for a property during inspection; y-axis represents density or frequency of the predicted probabilities or aggregated counts.

The dark black line presents the distribution of the observed outcome ($y$), which is a smoothed estimate of the distribution of binary response 'violation'. On the other hand, the light blue lines represent the posterior predictive simulations, which are the density of the replicated data ($y_{rep}$) generated from the posterior predictive distribution of the fitted model.

Whether the black line matches well with the blue lines indicates how well the model fits the observed data. If the black line aligns well with the blue lines, it suggests that the model is performing well in capturing the actual data distribution, and vice versa.

@fig-ppcheck shows the posterior predictive checks for the Bayesian model.

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheck
#| fig-cap: "Posterior Prediction Check"

pp_check(model) +
  theme_classic() +
  theme(legend.position = "bottom")
```

The plot shows that the curves for $y$ (observed data) and $y_rep$ (posterior predictive distribution) align closely with each other, suggesting that the fix effects of two predictor variables capture the overall pattern of the observed data well, and the Bayesian model generates predictions consistent with the observed data. Lack of mismatches between curves mean that the model provides good fit of data. Near extreme probabilities of 0 and 1, two curves tightly follow each other, indicating that the model correctly predicts extreme outcomes.

## Posterior vs Prior

Comparing the posterior distribution with the prior one is also necessary for model validation. It examines how the model fits and is affected by the data.

Prior distribution represents the beliefs about the parameter values before observing any data, which is constructed by our initial assumptions. Posterior distribution reflects updated beliefs about the parameters after observing the data.

In the plot, the posterior distribution is demonstrated on the left side, and the prior distribution is on the right side. Y-axis shows every parameter included in the model, each colored dot on the graph represents a parameter, and the horizontal line indicates the uncertainty.

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-posteriorvsprior
#| fig-cap: "Comparing the Posterior with the Prior"

#posterior_vs_prior(model) +
#  theme_minimal() +
#  scale_color_brewer(palette = "Set1") +
#  theme(legend.position = "bottom") +
#  coord_flip()
```

@fig-posteriorvsprior, compares the posterior with the prior distribution of the model, validating whether data has a significant impact on the parameter estimates and whether the model is well-fit.

Shown by the red dot representing "intercept", the narrower posterior compares to the prior one suggests that the model provide good estimate in baseline.

Shown by the blue dot representing predictor variable 'date_num', the posterior mean is close to 0, indicating little effect of it on the probability of violations. On the other hand, the credible interval is much narrower than the prior, reflecting strong eveidence from the data.

The rest of dots representing different levels of predictor variable 'property_type' show various posterior means and credible intervals. For instance, for high-rise buildings, the posterior mean is positive, indicating that high-rise buildings have higher log-odds of violations than the reference category. In general, each level shows a narrower posterior distribution than the prior, reflecting that the uncertainty decreases and the posterior distributions center around data-driven values.

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

#plot(first_model, "trace")

#plot(first_model, "rhat")
```

\newpage

# References

### 2024-11-26 scripts/06-model_data.R
Updated modeling script

@@ -1,37 +1,49 @@
 #### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Construct Bayesian Model for fire inspection outcome
+# Author: Yunkai Gu
+# Date: 24 November 2024
+# Contact: kylie.gu@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: Downloaded and cleaned data.
+# Any other information needed? None
 
 
 #### Workspace setup ####
 library(tidyverse)
+library(janitor)
+library(lubridate)
+library(broom)
+library(modelsummary)
 library(rstanarm)
+library(splines)
 
 #### Read data ####
-analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
+cleaned_data <- read_csv("data/02-analysis_data/fire_cleaned_data.csv")
+
 
 ### Model data ####
-first_model <-
-  stan_glm(
-    formula = flying_time ~ length + width,
-    data = analysis_data,
-    family = gaussian(),
-    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_aux = exponential(rate = 1, autoscale = TRUE),
-    seed = 853
+cleaned_data <- cleaned_data |>
+  mutate(
+    address_name = factor(address_name),
+    property_type = factor(property_type)
   )
 
+priors <- normal(0, 2.5, autoscale = TRUE)
 
-#### Save model ####
-saveRDS(
-  first_model,
-  file = "models/first_model.rds"
+bayesian_model_1 <- stan_glm(
+  formula = violation ~ date_num + property_type,
+  data = cleaned_data,
+  family = binomial(link = "logit"),
+  prior = priors,
+  prior_intercept = priors,
+  seed = 123,
+  cores = 4,
+  adapt_delta = 0.95,
+  iter = 2000
 )
 
+saveRDS(
+  bayesian_model_1,
+  file = "models/model_1.rds"
+)
 

### 2024-11-28 paper/paper.qmd
Updated data, model sections and  appendix for model

@@
 toc: true
+prefer-html: true
 bibliography: references.bib
@@
 library(knitr)
+library(kableExtra)
 library(RColorBrewer)
+library(broom.mixed)
 
 # Read the cleaned data
+cleaned_data <- read_csv(
+  file = here::here("data/02-analysis_data/fire_cleaned_data.csv")
+  )
 data <- read_csv(
@@
 
-$$ \text{logit}(p_i) = \beta_0 + \beta_1 \cdot \text{date}_i + \beta_2 \cdot \text{type}_i $$
-$$ \text{logit}(p_i) = \log\left(\frac{p_i}{1 - p_i}\right) $$
-$$ \beta_0 \sim \mbox{Normal}(0, 2.5) $$
-$$ \beta_1 \sim \mbox{Normal}(0, 2.5) $$
-$$ \beta_2 \sim \mbox{Normal}(0, 2.5) $$
+\begin{align} 
+\text{logit}(p_i) = \beta_0 + \beta_1 \cdot \text{date}_i + \beta_2 \cdot \text{type}_i \\
+\text{logit}(p_i) = \log\left(\frac{p_i}{1 - p_i}\right) \\
+\beta_0 \sim \mbox{Normal}(0, 2.5) \\
+\beta_1 \sim \mbox{Normal}(0, 2.5) \\
+\beta_2 \sim \mbox{Normal}(0, 2.5)
+\end{align}
 
@@
 - $\text{logit}(p_i) = \log\left(\frac{p_i}{1 - p_i}\right)$ is the log-odds of $p_i$.
-- $\beta_0$ is the intercept term of the Bayesian logistic regression, representing the baseline log-odds of a violation when `date_num = 0` and `property_type` is the reference category.
+- $\beta_0$ is the intercept term of the Bayesian logistic regression, representing the baseline log-odds of a violation when 'date_num = 0' and 'property_type' is the reference category.
 Formula (2) specifies that $\beta_0$ follows normal distribution with mean equals 0 and variance equals $2.5^2$.
-- $\beta_1$ is the coefficient for predictor variable `date_num`, representing the change in log-odds of a violation per unit increase in `date_num`, the inspection time interval.
+- $\beta_1$ is the coefficient for predictor variable 'date_num‘, representing the change in log-odds of a violation per unit increase in 'date_num', the inspection time interval.
 Formula (3) specifies that $\beta_1$ follows normal distribution with mean equals 0 and variance equals $2.5^2$.
-- $\beta_2$ is the coefficient for predictor variable `property_type`, representing the change in log-odds of a violation per unit increase in `property_type`.
+- $\beta_2$ is the coefficient for predictor variable ’property_type', representing the change in log-odds of a violation per unit increase in 'property_type'.
 Formula (4) specifies that $\beta_2$ follows normal distribution with mean equals 0 and variance equals $2.5^2$.
@@
 
-The prior of $Normal(0,2.5)$ for every coefficients is also reasonable because it reflects prior knowledge that most predictors have small-to-moderate effects on the log-odds scale.
+The prior of $\mbox{Normal}(0, 2.5)$ for every coefficients is also reasonable because it reflects prior knowledge that most predictors have small-to-moderate effects on the log-odds scale.
 This assumption would avoid overfitting to extreme values.
@@
 
+## Model Summary
+
 Our results are summarized in @tbl-modelresults.
@@
 model <-
-  readRDS(file = here::here("models/model_1.rds"))
+  readRDS(file = here::here("models/violation_prediction_model.rds"))
 ```
@@
 #)
+```
+
+## Posterior Parameter Estimates
+
+```{r}
+#| echo: false
+#| eval: true
+#| label: tbl-posteriorestimate
+#| tbl-cap: "Posterior Parameter Estimates"
+#| warning: false
+
+# Summarize the Bayesian model
+summary_stats <- summary(model)
+
+# Use `tidy()` for a clean tabular format
+library(broom.mixed)
+tidy_stats <- tidy(model, conf.int = TRUE)
+
+# Create a table of parameter estimates
+library(knitr)
+
+tidy_stats %>%
+  kable(format = "simple", col.names = c("Parameter", "Estimate", "Std.Error", "Conf.Low", "Conf.High"))
+
+```
+
+## Distribution of Predicted Probabilities
+
+@fig-predictprob plots the distribution of predicted probabilities for the model.
+X-axis represents the predicted probabilities ($p_i$) of the outcome for each observation in the dataset, and the values of probabilities are bounded from 0 to 1.
+Y-axis represents the relative density of observations iwth particular predicted probabilities.The density curve on the graph represents the estimated density of predicted probabilities, and the curve's height reflects how concentrated the predicted probabilities are around specific values.
+
+In general, the distribution shown by the plot has two peaks near 0 and 1, with very few probabilities in the intermediate range (0.25–0.75).
+This is a bimodal distribution, meaning that most observations are confidently predicted to either not have a violation ($p\approx0$) or have a violation ($p\approx1$).
+The sparse region in the intermediate range suggests that the model is making confident predictions, with minimal uncertainty for most observations.
+
+The plot shows that the distribution has higher peak, which also means higher density, around $p=1$.
+On the other hand, the peak around $p = 0$ is slightly lower.
+This indicates more confident predictions for observations with a high probability of a violation, meaning that the model predicts a larger proportion of observations with high confidence that a violation is likely to occur.
+
+Therefore, the conclusion drawn from the graph is that: more observations are predicted to have a high probability (mostly $p>0.9$) of being observed to have a violation.
+
+```{r}
+#| label: fig-predictprob
+#| fig-cap: Distribution of Predicted Probabilities
+#| echo: false
+#| warning: false
+#| message: false
+
+# Generate predicted probabilities
+predicted_probs <- posterior_predict(model)
+
+# Visualize predicted probabilities
+ggplot(
+  data = data.frame(predicted_probs = as.vector(predicted_probs)), 
+  aes(x = predicted_probs)
+  ) +
+  geom_density(fill = "blue", alpha = 0.5) +
+  labs(x = "Predicted Probability",
+       y = "Density") +
+  theme_minimal()
 ```
@@
 Prior distribution represents the beliefs about the parameter values before observing any data, which is constructed by our initial assumptions.
+In the plot, it is represented by horizontal lines with points centered at the prior mean (in this case, 0) in the right panel.
+
 Posterior distribution reflects updated beliefs about the parameters after observing the data.
-
-In the plot, the posterior distribution is demonstrated on the left side, and the prior distribution is on the right side.
-Y-axis shows every parameter included in the model, each colored dot on the graph represents a parameter, and the horizontal line indicates the uncertainty.
+It is represented by points (means or medians), which have colors representing the parameters respectively, and horizontal lines, which are credible intervals, derived from the data.
+The shorter horizontal lines, the narrower credible intervals, the more the reduced uncertainty for the parameter estimation after incorporating the data.
 
@@
 
-#posterior_vs_prior(model) +
-#  theme_minimal() +
-#  scale_color_brewer(palette = "Set1") +
-#  theme(legend.position = "bottom") +
-#  coord_flip()
+posterior_vs_prior(model) +
+  theme_minimal() +
+  theme(legend.position = "bottom") +
+  coord_flip()
 ```
 
-@fig-posteriorvsprior, compares the posterior with the prior distribution of the model, validating whether data has a significant impact on the parameter estimates and whether the model is well-fit.
+@fig-posteriorvsprior compares the posterior with the prior distribution of the Bayesian model included in this paper, validating whether the data has a significant impact on the parameter estimates and whether the model is well-fit.
 
-Shown by the red dot representing "intercept", the narrower posterior compares to the prior one suggests that the model provide good estimate in baseline.
+In general, each level shows a narrower posterior distribution than the prior, reflecting that the uncertainty decreases and the data provides substantial information to update the prior beliefs.
+Parameters with credible intervals far from zero in the posterior are strongly influenced by the data and have meaningful effects, such as property type of 'Rooming House' (prprty_typRH) and 'Group Home' (prprty_typeGH).
 
-Shown by the blue dot representing predictor variable 'date_num', the posterior mean is close to 0, indicating little effect of it on the probability of violations.
-On the other hand, the credible interval is much narrower than the prior, reflecting strong eveidence from the data.
+Shown by the point representing 'Intercept', the posterior credible interval is narrower than the prior, suggesting strong data support for it.
+The negative posterior mean indicates that the baseline log-odds of a violation for the reference property type (when date_num = 0) is below 0 (i.e., a low probability of violation).
 
-The rest of dots representing different levels of predictor variable 'property_type' show various posterior means and credible intervals.
-For instance, for high-rise buildings, the posterior mean is positive, indicating that high-rise buildings have higher log-odds of violations than the reference category.
-In general, each level shows a narrower posterior distribution than the prior, reflecting that the uncertainty decreases and the posterior distributions center around data-driven values.
+The posterior point for date_num is very narrow and centered near 0, suggesting that the data indicates little or no effect of inspection time interval on the log-odds of a violation.
+The credible interval includes 0, reinforcing the lack of a strong relationship between date_num and violations.
+
+Each property type coefficient represents the deviation in log-odds from the reference category.
+
+For instance, The points representing 'Rooming House' (prprty_RH), 'High Rise' (prprty_HR) and 'Group Home' (prprty_GH), have posterior distribution above 0, suggesting that rooming houses, high-rise buildings and group homes are more likely to have violations than the reference category.
+Narrow credible intervals indicate strong data support.
+
+On the other hand, the point representing 'Nursing Home' (prprty_NH) have posteriors close to 0, suggesting their effects are small or negligible compared to the reference category.
+Narrow credible intervals still indicate strong data support.
+
+The rest of dots representing different levels of 'property type' show various posterior means and credible intervals.
+Most of the points are close to 0 or above 0, providing information about effects of different property types respectively.
 
@@
 
-@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...
+### Trace Plot
 
-@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...
+Trace plot shows samples from all the chains.
+
+In the trance plot, x-axis represents the iteration numbers of the MCMC progress (in this case, up to 4000 iterations per chain), and y-axis displays the sampled values of the posterior distribution for each parameter.
+Each MCMC chain used during sampling is represented by a different color or line style..
+
+If all chains appear to oscillate around the same mean, and overlap significantly, it suggests that the parameter estimates are stable around a consistent mean.
+It is also a good sign if the chains have overlap in most regions and move freely across the posterior distribution.
+There should also be no systematic patterns, trends or large jumps.
 
@@
 #| warning: false
-#| label: fig-stanareyouokay
-#| fig-cap: "Checking the convergence of the MCMC algorithm"
-#| fig-subcap: ["Trace plot", "Rhat plot"]
-#| layout-ncol: 2
+#| label: fig-trace
+#| fig-cap: "Checking the Convergence of the MCMC Algorithm by Trace Plot"
 
-#plot(first_model, "trace")
+plot(model, "trace")
+```
 
-#plot(first_model, "rhat")
+@fig-trace shows the trace plot for the Bayesian model used in this paper.
+The chains for all parameters appear to mix well, with no signs of one chain dominating or exploring a different region of the parameter space.
+The parameters, especially 'Intercept' and 'date_num', show overlapping chains, which is a positive sign of convergence.
+
+Moreover, most chains is stabilized and oscillates around a consistent mean.
+The consistent behavior across iterations indciates that the chains have reached stationarity.
+Also, there are no visible divergences or chain-specific trends, suggesting the sampling process is functioning correctly.
+
+In general, the trace plots suggest that MCMC chains are converged, supported by good mixing, stationarity, and consistent sampling across chains, indicating that the posterior estimates for all parameters are likely reliable.
+Slight variability may be adjusted by more iterations, which aimed to gather additional independent samples.
+
+### R-hat Plot
+
+$\hat{R}$ is a diagnostic measure that compares the variance within each chain to the variance between chains.
+This diagnostic plot is used to asses the convergence of MCMC chains.Ideally, the $\hat{R}$ should be close to 1, so that chains have mixed well and are sampling from the same posterior distribution.
+For $\hat{R} \leq 1.5$, we could say that convergence is acceptable.
+
+@fig-rhat is the R-hat plot for the Bayesian model used in this paper.
+The plot shows that the R-hat values for all parameters are below 1.05, suggesting that the chains have converged well and are sampling effectively from the posterior distribution.
+The posterior samples are likely reliable for inference, indicating that the results are robust and can be used for interpreting parameter estimates.
+
+```{r}
+#| echo: false
+#| eval: true
+#| message: false
+#| warning: false
+#| label: fig-rhat
+#| fig-cap: "Checking the Convergence of the MCMC Algorithm by Rhat Plot"
+
+plot(model, "rhat")
 ```

### 2024-11-30 other/datasheet/datasheet_template.qmd
Added and updated datasheet for the dataset

---
title: "Datasheet for 'Highrise Residential Fire Inspection Results'"
subtitle: "Motivation, Composition, Collection Process, Preprocessing, Uses, Distribution, and Maintenence of the Dataset"
author: 
  - Yunkai Gu
thanks: "Code and data are available at: [https://github.com/Kylie309/Toronto-Fire-Inspection](https://github.com/Kylie309/Toronto-Fire-Inspection)."
date: today
date-format: long
format: pdf
number-sections: true
bibliography: references.bib
---

This datasheet extracts questions from @gebru2021datasheets.

The dataset discussed in this datasheet and used in the study is 'Highrise Residential Fire Inspection Results' [@fire_data], obtained from Open Data Toronto.

Relevant information could be found on the 'Fire Prevention – Inspection & Enforcement' page by City of Toronto [@fire_info].

**Motivation**

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    - The dataset was created to provide transparent data to present the results of fire safety inspections in all types of occupancies within Toronto conducted by the Fire Prevention Division, addressing violations of the Ontario Fire Code and other fire safety hazards within the authority of the Fire Protection and Prevention Act. 
    - Its purpose is to increase public safety and awareness of fire safety, and to offer open, accessible and structured information to the public and researchers. This dataset filled the lack of resources related to detailed fire inspection outcomes and violation status of fire safety regulations for different types of properties in Toronto.

2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - The dataset was created by The Fire Prevention Division, and was provided access to the public by the City of Toronto's Open Data Portal.

3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
    - The creation and maintenance of the dataset are funded by the City of Toronto through its Open Data Portal.

4. *Any other comments?*
    - None.

**Composition**

1. *What do the instances that comprise the dataset represent (for example, documents, photos, people, countries)? Are there multiple types of instances (for example, movies, users, and ratings; people and interactions between them; nodes and edges)? Please provide a description.*
	- Each instance in the dataset represents a fire inspection event for a residential property in Toronto and its result and outcome.
	- Each instance include details in three main aspects: property identifier (columns of 'PropertyAddress', 'ADDRESS_NUMBER', 'ADDRESS_NAME', 'PropertyType', 'propertyWard'), inspection information (columns of 'Enforcement_Proceedings', 'InspectionThread', 'INSPECTIONS_OPENDATE', 'INSPECTIONS_CLOSEDDATE'), and inspection outcomes (columns of 'VIOLATION_FIRE_CODE', 'VIOLATIONS_ITEM_NUMBER', 'VIOLATION_DESCRIPTION').

2. *How many instances are there in total (of each type, if appropriate)?*
	- There are 96821 instances in total in the dataset. This number changes as the dataset is updated with new inspections.

3. *Does the dataset contain all possible instances or is it a sample (not necessarily random) of instances from a larger set? If the dataset is a sample, then what is the larger set? Is the sample representative of the larger set (for example, geographic coverage)? If so, please describe how this representativeness was validated/verified. If it is not representative of the larger set, please describe why not (for example, to cover a more diverse range of instances, because instances were withheld or unavailable).*
	- The raw dataset downloaded from the Open Data Toronto Portal is not a subset or sample from another larger data set. It contains the results of all reported fire inspections in Toronto, and the work completed in 2020 has allowed for the expansion of the portal to not only show residential high-rise buildings but inspection matters for multi-unit residential occupancy types. The types are recorded in the 'PropertyType' column.
	- The cleaned dataset for this study, on the other hand, chose the cases whose inspection processes ended with all violations fixed within 2024. The columns selected to conduct study are the 'PropertyType', 'INSPECTIONS_OPENDATE', 'INSPECTIONS_CLOSEDDATE' and 'VIOLATIONS_ITEM_NUMBER' columns.

4. *What data does each instance consist of? "Raw" data (for example, unprocessed text or images) or features? In either case, please provide a description.*
	- Each instance consist of details in three main aspects: property identifier (columns of 'PropertyAddress', 'ADDRESS_NUMBER', 'ADDRESS_NAME', 'PropertyType', 'propertyWard'), inspection information (columns of 'Enforcement_Proceedings', 'InspectionThread', 'INSPECTIONS_OPENDATE', 'INSPECTIONS_CLOSEDDATE'), and inspection outcomes (columns of 'VIOLATION_FIRE_CODE', 'VIOLATIONS_ITEM_NUMBER', 'VIOLATION_DESCRIPTION').

5. *Is there a label or target associated with each instance? If so, please provide a description.*
	- The target is the violation status of the fire safety checks for each residential property inspected. 
	- Three columns act as the label: 'VIOLATION_FIRE_CODE'	presents fire code under which violation was noted; 'VIOLATIONS_ITEM_NUMBER' presents the order number of violations by code, and 0 if no violations observed; 'VIOLATION_DESCRIPTION' presents description of fire code under which violation was noted.

6. *Is any information missing from individual instances? If so, please provide a description, explaining why this information is missing (for example, because it was unavailable). This does not include intentionally removed information, but might include, for example, redacted text.*
	- Some individual instances do not have the information of inspection closed date due to incomplete records. Also, if there is no violation inspected for one case, 'VIOLATION_FIRE_CODE' and 'VIOLATION_DESCRIPTION' columns will include NA values.

7. *Are relationships between individual instances made explicit (for example, users' movie ratings, social network links)? If so, please describe how these relationships are made explicit.*
	- Relationships between instances are not defined explicitly.

8. *Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.*
	- The dataset does not include predefined splits. People downloaded the dataset could create splits by their own based on different aspects of the features recorded, such as property types or geographic locations.

9. *Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.*
	- The dataset may include errors arising from manual data entry, such as inconsistent formatting, especially for column 'VIOLATION_DESCRIPTION' which describes the details of fire code violated by the property inspected.

10. *Is the dataset self-contained, or does it link to or otherwise rely on external resources (for example, websites, tweets, other datasets)? If it links to or relies on external resources, a) are there guarantees that they will exist, and remain constant, over time; b) are there official archival versions of the complete dataset (that is, including the external resources as they existed at the time the dataset was created); c) are there any restrictions (for example, licenses, fees) associated with any of the external resources that might apply to a dataset consumer? Please provide descriptions of all external resources and any restrictions associated with them, as well as links or other access points, as appropriate.*
	- The dataset is self-contained and the portal does not include any external resources linked to it.

11. *Does the dataset contain data that might be considered confidential (for example, data that is protected by legal privilege or by doctor-patient confidentiality, data that includes the content of individuals' non-public communications)? If so, please provide a description.*
	- The dataset does not contain confidential information. It focuses on property-level data and excludes personal, sensitive details.

12. *Does the dataset contain data that, if viewed directly, might be offensive, insulting, threatening, or might otherwise cause anxiety? If so, please describe why.*
	- The dataset does not contain directly offensive, insulting or threatening information. However, inspection outcomes related to violations of fire safety checks might cause anxiety for some readers.

13. *Does the dataset identify any sub-populations (for example, by age, gender)? If so, please describe how these subpopulations are identified and provide a description of their respective distributions within the dataset.*
	- The dataset does not identify data by sub-populations. It is focused on property-level information.
	- For the property-level information, populations could be segmented by the property types. There are ten residential occupancy types included in the dataset: high-rise, low-rise, rooming houses, group homes, hotels and motels, detention centres, hospitals, nursing homes, residential cares and group homes designated a VO. The latter 4 are applicable vulnerable occupancy buildings.

14. *Is it possible to identify individuals (that is, one or more natural persons), either directly or indirectly (that is, in combination with other data) from the dataset? If so, please describe how.*
	- No, it is not possible to identify individuals, either directly or indirectly, from the datase. The dataset does not include personal data that could be used to identify individuals.

15. *Does the dataset contain data that might be considered sensitive in any way (for example, data that reveals race or ethnic origins, sexual orientations, religious beliefs, political opinions or union memberships, or locations; financial or health data; biometric or genetic data; forms of government identification, such as social security numbers; criminal history)? If so, please provide a description.*
	- No, the dataset does not contain sensitive data of this nature. It is limited to fire safety and inspection information.

16. *Any other comments?*
	- While the dataset only contains property-level information and excludes personal and sensitive data, users should interpret the findings within appropriate contextual frameworks to avoid misinterpretation.

**Collection process**

1. *How was the data associated with each instance acquired? Was the data directly observable (for example, raw text, movie ratings), reported by subjects (for example, survey responses), or indirectly inferred/derived from other data (for example, part-of-speech tags, model-based guesses for age or language)? If the data was reported by subjects or indirectly inferred/derived from other data, was the data validated/verified? If so, please describe how.*
	- The data was directly observable. It presents the results and outcomes of fire inspections in Toronto collected by Toronto Fire Services, recording the observations of fire safety checks of the buildings and violations of regulations during inspections.

2. *What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)? How were these mechanisms or procedures validated?*
	- The data is collected by manual human curation. It shows properties where inspections have been conducted by a TFS Fire Inspector, including properties where violations have been found which are required to be fixed for compliance at the time with the Ontario Fire Code, FPPA and Municipal Code.

3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
	- The raw dataset downloaded from the Open Data Toronto Portal is not a subset or sample from another larger data set. It contains the results of all reported fire inspections in Toronto, and the work completed in 2020 has allowed for the expansion of the portal to not only show residential high-rise buildings but inspection matters for multi-unit residential occupancy types. The types are recorded in the 'PropertyType' column.
	- The cleaned dataset for this study, on the other hand, chose the cases whose inspection processes ended with all violations fixed within 2024. The columns selected to conduct study are the 'PropertyType', 'INSPECTIONS_OPENDATE', 'INSPECTIONS_CLOSEDDATE' and 'VIOLATIONS_ITEM_NUMBER' columns.

4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
	- Licensed fire inspectors employed by Toronto Fire Services were responsible for the data collection as part of their official duties.

5. *Over what timeframe was the data collected? Does this timeframe match the creation timeframe of the data associated with the instances (for example, recent crawl of old news articles)? If not, please describe the timeframe in which the data associated with the instances was created.*
	- The dataset includes the results of inspections over an ongoing timeframe, with updates reflecting new inspection activities. The earliest open date of the inspection case is 2017-01-02, and the newest inspection case has been closed at 2024-11-28.

6. *Were any ethical review processes conducted (for example, by an institutional review board)? If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- Ethical review processes were not explicitly mentioned. However, data collection follows  guidelines and privacy laws (e.g. City Information Management Policies and Legislation) to ensure ethical practices.

7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
	- The data was collected directly by fire inspectors manualy during fire safety inspections of residential buildings.

8. *Were the individuals in question notified about the data collection? If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
	- The website did not provide explicit information about how TFS notified the residents in the properties for inspections. It could be inferred that the Fire Prevention Division would make notifications about fire inspections through official channels.

9. *Did the individuals in question consent to the collection and use of their data? If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
	- The dataset includes to property-level information rather than personal data. Therefore, explicit individual consent was not applicable. The inspections are conducted under relevant regulatory authority and privacy regulations.

10. *If consent was obtained, were the consenting individuals provided with a mechanism to revoke their consent in the future or for certain uses? If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
	- Not applicable. The dataset does not involve personal data requiring consent.

11. *Has an analysis of the potential impact of the dataset and its use on data subjects (for example, a data protection impact analysis) been conducted? If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- There is no explicit mention of a data protection impact analysis. However, the dataset excludes personal data and the inspections have been conducted under privacy laws and supervisions by official government departments, minimizing potential risks.

12. *Any other comments?*
	- None.

**Preprocessing/cleaning/labeling**

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
	- Specific preprocessing/cleaning/labeling steps for the data are not explicitly documented.

2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
	- The truly "raw" data is not publicly available. The dataset provided on the Open Data Toronto Portal represents a cleaned table for public use.

3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
	- The software used to preprocess the "raw" data is currently not available. For the cleaning process included in this study, the dataset downloaded from the Open Data Toronto Portal is cleaned by R, and the script is included in `scripts/03-clean_data.R`.

4. *Any other comments?*
	- None.

**Uses**

1. *Has the dataset been used for any tasks already? If so, please provide a description.*
	- Currently, it is only posted to show open, accessible, transparent information of fire inspection results in Toronto by Toronto Fire Services to implement fire prevention and enforcement strategies and to increase public safety and awareness.

2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
	- Haven't found one yet.

3. *What (other) tasks could the dataset be used for?*
	- Other tasks the dataset could be used for includes: Analyzing trends in violations of fire safety regulations in properties across different neighborhoods and regions; Implementing targeted policy decisions in certain areas and for certain property types to improve fire safety measures; Visualizing regional trends of fire inspection results by mapping.

4. *Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses? For example, is there anything that a dataset consumer might need to know to avoid uses that could result in unfair treatment of individuals or groups (for example, stereotyping, quality of service issues) or other risks or harms (for example, legal risks, financial harms)? If so, please provide a description. Is there anything a dataset consumer could do to mitigate these risks or harms?*
	- The dataset focuses on property-level data and does not include personal information. This means that its risk of violating privacy regulations and resulting in unfair treatment of individuals is minimized.
	- Careful contextual and regional analysis are recommended to avoid misinterpretation.

5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
	- For instance, the dataset should not be used for predicting the fire safety check outcomes for tagreted individuals only, as it contains no personal data.

6. *Any other comments?*
	- The dataset is a starting point for fire safety analysis and public awareness, but its utility can be enhanced by combining it with other datasets, such as demographic data or information related to properties, to provide a more complete understanding of Toronto's fire safety dynamics.

**Distribution**

1. *Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created? If so, please provide a description.*
	- Yes, the dataset distributed to anyone since it is publicly available. Anyone could download it through the City of Toronto's Open Data Portal. The portal provides open, transparent and accessible information, aimed to increase public safety and awareness.

2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
	- The dataset is distributed through the Open Data Toronto Portal. It can be downloaded directly from the portal in three formats: CSV, JSON and XML. The portal also provides code snippets for accessing a dataset via the API. No DOI is available for this dataset.

3. *When will the dataset be distributed?*
	- The dataset is already available and continuously updated on the Open Data Toronto Portal.

4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
	- The data is distributed under the terms of the Open Government License - Toronto. The license writes that everyone is free to "copy, modify, publish, translate, adapt, distribute or otherwise use the Information in any medium, mode or format for any lawful purpose."
	- There's no fee associated with accessing the dataset.

5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
	- No third parties have imposed IP-based or other restrictions on the dataset. It is freely available under the terms of the Open Government License - Toronto.

6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
	- There are no export controls or other regulatory restrictions applied to the dataset or to individual instances.

7. *Any other comments?*
	- None.

**Maintenance**

1. *Who will be supporting/hosting/maintaining the dataset?*
	- The creation and maintenance of the dataset are supported and funded by the City of Toronto through its Open Data Portal.

2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- The contact information of the Fire Prevention Command offices is listed below:
	- North Command Wards: 6-York Centre, 8-Eglinton-Lawrence, 15-Don Valley West, 16 Don Valley East, 17-Don Valley North, 18-Willowdale, 5100 Yonge Street, Toronto, ON, M2N 5V7; Phone: 416-338-9150
	- East Command Wards: 14-Toronto-Danforth, 19-Beaches-East York, 20-Scarborough Southwest, 21-Scarborough Centre, 22-Scarborough-Agincourt, 23-Scarborough North, 24-Scarborough-Guildwood, 25-Scarborough-Rouge Park, 150 Borough Drive, Toronto, ON, M1P 4N7; Phone: 416-338-9250
	- South Command Wards: 9-Davenport, 10-Spadina-Fort York, 11-University-Rosedale, 12-Toronto-St.Paul’s, 13-Toronto Centre, City Hall Gr Fl, W., 100 Queen St.West, Toronto, ON, M5H 2N2; Phone: 416-338-9350
	- West Command Wards: 1-Etobicoke North, 2-Etobicoke Centre, 3-Etobicoke-Lakeshore, 4-Parkdale-High Park, 5-York South-Weston, 7-Humber River-Black Creek, 399 The West Mall, Toronto, ON, M9C 2Y2; Phone: 416-338-9450

3. *Is there an erratum? If so, please provide a link or other access point.*
	- None. Any corrections or updates to the dataset are directly posted and published on the Open Data Toronto's page of the dataset.

4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
	- Once there are new ongoing fire inspections and their results to be updated, the dataset would be changed by Toronto Fire Services. These changes will be directly communicated to the public through the Open Data Portal. Consumers can monitor the dataset page for version updates by viewing the "Data last refreshed" section on the page.

5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
	- The dataset primarily contains property-level information rather than personal data. Any associated personal information, such as contact details from inspections, is handled with reference to Toronto’s privacy and data retention policies, as outlined in their privacy guidelines.

6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
	- Older versions of the dataset are not typically maintained.

7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
	- Since the dataset is complete created and contributed by Toronto Fire Services in City of Toronto, extensions and contributions cannot be directly made through the Open Data Portal. But potential questions, comments, and suggestions for improvement could be sent to the Open Data Team on [Twitter](https://x.com/open_to), [GitHub](https://github.com/open-data-toronto/wp-open-data-toronto), [Medium](https://medium.com/open-data-toronto), or via e-mail [opendata@toronto.ca](opendata@toronto.ca).

8. *Any other comments?*
	- None.

\newpage

# References

### 2024-12-01 paper/paper.qmd
Updated survey section in appendix

@@
   )
+
 ```
@@
 
-We use the statistical programming language R [@citeR]....
+Note that though the dataset named "Highrise" Residential Fire Inspection Results, expansion work completed in 2020 has allowed for inspection results for more prperty types to be presented in the dataset.
+The portal now not only shows residential high-rise buildings, but also shows "inspection matters for multi-unit residential occupancy types including high-rise, low-rise, small multi-unit buildings, rooming houses/group homes, hotels, motels, detention centres, and all applicable vulnerable occupancy buildings (hospitals, nursing homes, residential cares and group homes designated a VO)" [@fire_info].
+
+To ensure the analysis presented in this paper remains relevant and current, only inspection cases that have concluded their inspection files or enforcement proceedings within the year 2024 are selected.
+This is achieved by filtering the dataset to keep only rows where the 'INSPECTIONS_CLOSEDDATE' column displays a date that falls within the year 2024.
+This approach ensures that the data reflects the most recent developments, providing an up-to-date basis for analysis and maintaining a clear and accurate representation of the latest trends and outcomes in fire safety checks.
+
+More detailed data cleaning process is included in [Appendix -@sec-appx-data].
+
+The analyses presented in this paper were conducted using R programming language [@citeR].
+The `tidyverse` packages [@citetidyverse] were used in the process of data simulation, testing beforehand.
+After the original raw data was downloaded by using `tidyverse` package [@citetidyverse], data cleaning process was done by using `tidyverse` package [@citetidyverse], `lubridate` package [@citelubridate], and `arrow` package [@citearrow].
+We use `testthat` package [@citetest] to develop the test for structure and format of simulation and analysis data.
+
+Then, models were constructed using `tidyverse` package [@citetidyverse], `lubridate` package [@citelubridate] and `rstanarm` [@citerstanarm] package.
+The model results were then presented by both the tables and graphs.
+Tables were made with `modelsummary` [@citemodelsummary] package, `broom.mixed` [@citebroom] package, `dplyr` [@citedplyr] package and `knitr` package.
+Graphs were made with `ggplot2` package [@citeggplot] and `RColorBrewer` package [@citercolorbrewer].
 
@@
 
+## Violation by Property Type
+
+@fig-violationbytype depicts faceted bar plots showing the distribution of violation statuses (0 for no violation, 1 for violation) across different property types.
+Each subplot corresponds to a different property type.
+
+In general, property types of "Group Home," "High Rise," "Low Rise," and "Rooming House," have a higher proportion of violations (1).
+The type "Hotel & Motel" has balanced counts between 0 and 1, but violations (1) are slightly more frequent.
+These property types may require more attention or stricter inspections.
+
+The other property types, especially "Detention" and "Nursing Home", show a much lower proportion of violations, suggesting fewer relative violation ratio.
+
+```{r}
+#| label: fig-violationbytype
+#| fig-cap: Violation Status by Property Type
+#| echo: false
+#| warning: false
+#| message: false
+
+data |> 
+  ggplot(aes(x = as.factor(violation), fill = as.factor(violation))) +
+  geom_bar(color = "black") +
+  facet_wrap(~ property_type, scales = "free_y") + # Create one subplot per property type
+  labs(
+    x = "Violation Status",
+    y = "Count",
+    fill = "Violation Status"
+  ) +
+  theme_minimal() +
+  theme(
+    axis.text.x = element_text(size = 10),
+    axis.text.y = element_blank(), 
+    axis.title.x = element_text(size = 12),
+    axis.title.y = element_text(size = 12),
+    strip.text = element_text(size = 8), 
+    legend.title = element_text(size = 12),
+    legend.text = element_text(size = 10),
+    panel.spacing = unit(1, "lines")
+  ) +
+  scale_fill_manual(values = c("skyblue", "orange"))
+```
+
 # Model
@@
 
-Our results are summarized in @tbl-modelresults.
+Our results of the Bayesian logistic regression model are summarized in @tbl-modelresults. The table provides information of coefficients and main summary statistics.
+
+The table firstly lists estimates of coefficients for all parameters.
+The first line suggests an intercept of -6.72 for the model, indicating very low baseline odds of a violation for the reference property type when date_num = 0.
+The second line presents that the estimated coefficient for date_num is 0.02, which is very small and suggests that the inspection time interval has negligible effect on the violation outcome of observations.
+
+Then the table shows the coefficients for every property type respectively.
+All property types show large positive coefficients, meaning that they increase the log-odds of violations and have higher risk of violation compared to the reference property type.
+For instance, for property type of "Group Home", it increases log-odds of violation by 5.88; for property type of "High Rise", it increases log-odds of violation by 6.21; for property type of "Hospital", it increases log-odds of violation by 4.67; etc.
+It could be observed that "Nursing Home" has the smallest coefficient, and thus has the smallest effect on violation.
+However, it still contribute positively to the log-odds.
+
+The table also presents summary statistics of the model.
+One of the important results include $R^2=0.342$.
+$R^2$ is the proportion of the variation in the dependent variable that is predictable from the independent variables [@wiki_rsquare].
+R-squared of 0.342 suggests that 34.2% of the variability in the response variable (violation) is explained by the model, which is relatively good for logistic regression.
+Moreover, the RMSE (Root Mean Squared Error) value of 0.32 shows the average deviation between predicted probabilities and observed outcomes.
+This value is low, indicates a satisfactory fit for the model.
 
@@
 #| label: tbl-modelresults
-#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
+#| tbl-cap: "Explanatory Models of Probability of Violation based on Inspection Time Interval and Property Type"
 #| warning: false
@@
 modelsummary::modelsummary(
-  models = model,
+  list(
+    "Model" = model
+  ),
   statistic = "mad",
@@
 )
-
-#modelsummary::modelsummary(
-#  list(
-#    "First model" = model,
-#  ),
-#  statistic = "mad",
-#  fmt = 2
-#)
 ```
@@
 ## Posterior Parameter Estimates
+
+@tbl-posteriorestimate shows more detailed information about the coefficients of each parameter.
+Column "Estimate" presents the mean posterior estimate for the effect of each parameter on the log-odds of the outcome (violation); "Std.Error" presents the standard deviationor the uncertainty in the estimate; "Conf.Low" and "Conf.High" are the lower and upper bounds of the 95% credible interval for the parameter, showing the range of plausible values.
 
@@
 
+# Round all numeric columns to 3 decimal places
+library(dplyr)
+tidy_stats <- tidy_stats %>%
+  mutate(across(where(is.numeric), ~ round(., 3)))
+
 # Create a table of parameter estimates
@@
 
+```
+
+Main interpretation for this code focuses on 95% confidence interval.
+In general, if the credible interval does not include 0, the effect of the variable is statistically significant, indicating that the model is confident about the relationship.
+Most of the parameters have credible intervals excluding value 0, and some intervals are far from 0, suggesting that there's strong evidence supporting their effect on the violation outcome.
+For instance, the property type of "High Rise" has 95% CI of $[3.25, 10.45]$, showing that the model is confident about the significant effect of the increased contribution by high rise buildings to log-odds of violations.
+
+On the other hand, a few parameters have 95% confidence interval including 0, such as property types of "Group Home", "Group Home (VO)", "Nursing Home".
+This represents that the effect of the variables on violations is not statistically significant, and the relationship is uncertain.
+Further data collection may be needed to better understand their relationship with violations.
+
+@fig-95ci visualizes the parameter estimate values and their credible intervals for easier presentation.
+
+```{r}
+#| label: fig-95ci
+#| fig-cap: Parameter Estimates with 95% Credible Intervals
+#| echo: false
+#| warning: false
+#| message: false
+
+tidy_stats |>
+  ggplot(aes(x = term, y = estimate)) +
+  geom_point(size = 3, color = "red") +
+  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
+  coord_flip() +
+  labs(y = "Log-Odds Estimate",
+       x = "Parameter") +
+  theme_minimal()
 ```
@@
 
-# Additional data details
+# Surveys, Sampling, and Observational Data
+
+## Overview of the Idealized Fire Safety Resident Survey
+
+Fire safety inspections in residential buildings provide a critical mechanism for ensuring compliance with fire safety regulations.
+However, the dataset presenting inspection outcomes and analysis based on it only reflects the violation status before the enforcement procedure ends.
+It fails to provide information about whether buildings will maintain compliance or revert to unsafe practices after the inspection process ends.
+Since frequent routine inspections are often expensive and therefore impossible, it is necessary to explore alternative methods for monitoring the fire safety status of the properties and evaluating the long-term effectiveness of previous inspections.
+
+Introducing a resident survey fills these gaps by collecting the experiences and insights of those who are most directly affected by fire safety measures.
+Residents live in these buildings are familiar with the day-to-day reality of fire safety status, and could provide honest feedback and valuable perspective on whether inspections have resulted in improvements, or whether the properties conduct actions that violate regulations again.
+
+This approach not only offers real-time updates of the violation status of the properties, but is also cost-effective.
+By incorporating resident surveys, the monitoring process becomes more sustainable, enhancing the overall understanding of fire safety compliance beyond the inspection period.
+
+The fire resident survey is designed to achieve the following objectives:
+
+- Assess Perceived Changes After Inspections: Determine if residents have noticed any improvements or changes in fire safety measures after the inspection and enforcement procedure ends, offering valuable feedback on the effectiveness of the interventions made.
+
+- Identify Recurring Issues in Residential Buildings: Collect residents' observations and feedback on recurring violations of fire safety regulations in the properties, helping to highlight areas that may need further attention or action.
+
+- Improve Policies Related to Fire Safety: Provide down-to-earth perspective from residents to improve regulatory practices related to fire safety, ensuring that policies are better aligned with the needs and experiences of those directly affected.
+This can also guide more effective resource allocation to address ongoing safety concerns.
+
+- Arise Residents' Awareness of Fire Safety: Determine whether residents are aware that a fire safety inspection has taken place in their buildings, and to what extent residents recognizes the importance of fire safety.
+The survey, therefore, aimed to emphasize to residents that fire safety inspections are not just a property-level concern, but an issue that affects everyone living in the building.
+By highlighting the collective responsibility for fire safety, the survey sought to encourage residents to take an active role in the ongoing maintenance and improvement of fire prevention measures, and to promote voluntary compliance with fire safety regulations, ensuring that all residents contribute to maintaining a safe living environment for everyone in the building.
+
+## Survey
+
+This survey will be conducted using Google Forms, which is an effective platform for data collection. The survey can be accessed by the link, [Google Form Survey].
+
+### Survey Structure
+
+**Title:**
+
+Fire Safety Feedback Survey for Residential Properties in Toronto
+
+**Introduction:**
+
+We are conducting a survey to evaluate fire safety measures in your building following recent fire safety inspections conducted by Toronto Fire Services.
+
+Your feedback will help us assess the effectiveness of inspections, identify any ongoing safety concerns, and improve fire safety standards.
+
+**Please note:**
+
+- Your answers will all be treated with complete confidentiality and anonymity.
+
+- Participation in this survey is voluntary.
+
+- We encourage you to provide honest and thoughtful responses.
+
+- The survey is estimated to take about 10 minutes to complete.
+
+- If you have any questions or concerns, feel free to contact [kylie.gu@mail.utoronto.ca](kylie.gu@mail.utoronto.ca)  (Yunkai Gu).
+
+Thank you for your valuable input. Your responses are essential for evaluating the outcomes and results of fire safety inspections by TFS.
+
+**Section 1: Residential Building Information**
+
+What is your city of residence?
+
+- Toronto
+
+- Other (End Survey)
+
+What is your address? (Please specify to street number)
+
+[Answer Box]
+
+What is the occupancy type of your residential property?
+
+- High Rise
+
+- Low Rise
+
+- Rooming House
+
+- Group Home
+
+- Group Home (VO)
+
+- Hotels and Motels
+
+- Detension
+
+- Hospital
+
+- Nursing Home
+
+- Residential Cares
+
+- Other [Answer Box]
+
+- Unsure
+
+What is your duration of residence? (Optional)
+
+- Less than 1 year
+
+- 1 to 3 years
+
+- 3 to 5 years
+
+- More than 5 years
+
+**Section 2: Awareness of Fire Safety Inspection**
+
+Were you aware that a fire safety inspection was recently conducted in your building?
+
+- Yes
+
+- No (Skip Next 2 Questions and Section 3)
+
+If so, please indicate the source of awareness if available: (Optional; Select All That Apply)
+
+- Notification from building management
+
+- Signs posted in the building
+
+- From neighbors/friends
+
+- Other [Answer Box]
+
+If so, please indicate the date of the inspection if available: (Optional; If you don't know, please leave the box blank.)
+
+[Answer Box]
+
+**Section 3: Improvements and Changes After Inspection**
+
+Have you observed any improvements in fire safety facilities? (Select All That Apply)
+
+- Fire alarms were tested or replaced.
+
+- Emergency exits were cleared or repaired.
+
+- Fire extinguishers were checked or replaced.
+
+- Sprinkler systems were serviced.
+
+- Other [answer box]
+
+- No noticeable changes.
+
+On a scale of 1 to 5, how effective do you think the changes have been in improving fire safety in your building?
+
+[Scale 1-5]
+
+Do you have any thoughts or suggestions regarding the fire safety inspection conducted by TFS? (Optional)
+
+[Answer Box]
+
+**Section 4: Current Fire Safety Conditions**
+
+On a scale of 1 to 5, how confident are you in your building’s current compliance with fire safety standards?
+
+[Scale 1-5]
+
+How is the fire alarm functionality in your building?
+
+- Fire alarms are always functional.
+
+- Fire alarms are sometimes not functional.
+
+- Fire alarms are often not functional.
+
+- Fire alarms are always not functional.
+
+- Unsure.
+
+- Other [Answer Box]
+
+Are the fire alarms in your building regularly tested?
+
+- Yes
+
+- No
+
+- Unsure
+
+How is the emergency exit accessibility in your building?
+
+- Emergency exits are always accessible.
+
+- Emergency exits are sometimes blocked or locked.
+
+- Emergency exits are often blocked or locked.
+
+- Emergency exits are always blocked or locked.
+
+- Unsure
+
+- Other [Answer Box]
+
+How is the fire extinguisher functionality in your building?
+
+- Fire extinguishers are always functional.
+
+- Fire extinguishers are sometimes not functional.
+
+- Fire extinguishers are often not functional.
+
+- Fire extinguishers are always not functional.
+
+- Unsure.
+
+- Other [Answer Box]
+
+Are fire extinguishers easily accessible and appear to be in working condition in your building?
+
+- Yes
+
+- No
+
+- Unsure
+
+How is the sprinkler system functionality in your building?
+
+- Sprinkler systems are always functional.
+
+- Sprinkler systems are sometimes not functional.
+
+- Sprinkler systems are often not functional.
+
+- Sprinkler systems are always not functional.
+
+- Unsure.
+
+- Other [Answer Box]
+
+Are the sprinkler systems in your building regularly maintained?
+
+- Yes
+
+- No
+
+- Unsure
+
+Have you noticed any fire safety concerns in your building?
+
+- Yes
+
+- No
+
+If so, please describe the fire safety concerns you noticed. (Optional)
+
+[Answer Box]
+
+**Section 5: Resident Experiences and Suggestions**
+
+Have you participated in any activities related to fire safety organized by the building management (e.g. a fire emergency preparedness training in your building)?
+
+- Yes
+
+- No
+
+Have you received any notifications from the building management regarding fire safety inspection and/or awareness?
+
+- Yes
+
+- No
+
+Do you have any suggestions for enhancing fire safety in your building? (Optional)
+
+ [Answer Box]
+
+**End Message:**
+
+Thank you for completing the Fire Safety Feedback Survey.
+Your responses will help us better evaluate the effectiveness of fire safety inspections by TFS, understand fire safety conditions in your residential building, and improve measures to protect residents like you.
+
+If you have any further questions or concerns, please feel free to contact [kylie.gu@mail.utoronto.ca](kylie.gu@mail.utoronto.ca).
+
+### Survey Design Considerations: Biases and Solutions
+
+The designing process of the survey has drawn from the guidance in the paper “How to Run Surveys” [@howtorunsurveys].
+The following considerations address the potential biases in the proposed resident survey on fire safety compliance and suggest practical solutions:
+
+- Response Bias
+
+This type of bias occurs as respondents "try to take short cuts to minimize the cognitive load" [@howtorunsurveys].
+They may also be natural consequences of how people process information based on the serial position of alternatives and their visual presentation.
+Typical bias includes: moderacy biases, extreme response biases, and response Order biases.
+In other words, respondents may consistently select moderate or extreme options, or may be influenced by the order in which options are presented.
+
+Stefanie Stantcheva suggests that randomizing the order of response options for questions with unordered (nominal) response options would be one of the solutions to the response biases.
+According to this recommendation, the fire safety feedback survey has been designed to randomly arrange the order of options for questions related to functionality and accessibility of fire safety facilities in the buildings in section 4.
+These questions followed a consistent and same structure and logic, making them particularly vulnerable to response biases due to the potential influence of the order in which options are presented.
+Randomizing the response options mitigates effects for such biases, enhancing the reliability of the data collected.
+
+Stefanie Stantcheva also recommends avoiding long response lists, as they can overwhelm respondents and introduce bias.
+Therefore, most of the survey questions do not require respondents to read through extensive lists of alternatives and choices, unless necessary.
+This approach aims to enhance the clarity and make respondents feel less stressful in completing the survey.
+
+Balanced scales, such as a 5-point Likert scale with clear and evenly distributed options, could also help reduce the negative effects of the response bias by providing a range of numeric, direct choices to the respondents.
+In accordance with this principle, the survey includes several scaled questions, such as "On a scale of 1 to 5, how effective do you think the changes have been in improving fire safety in your building?"
+
+- Social Desirability Bias
+
+Social Desirability Bias (SDB) typically stems from the desire of respondents to avoid embarrassment and project a favorable image to others, resulting in respondents not revealing their actual attitudes [@howtorunsurveys].
+Respondents may provide answers they believe are socially acceptable or align with what they perceive the surveyor expects.
+
+Stefanie Stantcheva suggests that by assuring respondents of complete anonymity in the survey, the social desirability biases could be mitigated, since emphasizing the confidentiality of responses would reduce pressure for the respondents to conform.
+
+According to this advice, the fire safety feedback survey has included special emphasis on anonymity at the beginning in the introduction section, clearly informing respondents that their answers "will all be treated with complete confidentiality and anonymity." This assurance is intended to encourage honest and open responses, helping to aviod situations where respondents provide socially desirable answers rather than their true opinions.
+
+This fire safety feedback survey also uses neutral wording and avoids leading questions.
+For instance, instead of asking, “Do you think the building is safer now?”, the survey asks, “Have you noticed any changes in safety measures?” This approach ensures that respondents are not influenced by biased or suggestive language, allowing them to provide more objective and accurate feedback based on their own observations and thoughts.
+
+- Attrition or Non-response Bias
+
+Not all residents will respond to the survey, and some may drop out midway, leading to missing data or biased outcomes.
+Attrition is a special case of non-response bias, which refers to the phenomenon of respondents dropping out of the study before completing it [@howtorunsurveys].
+
+As recommended by Stefanie Stantcheva, the fire safety feedback survey is designed to provide a smooth respondent experience, ensuring that the survey is visually clear and user-friendly to reduce dropout rates.
+The survey only includes only necessary, non-complex questions to keep it concise and short, ensuring that respondents do not feel overwhelmed or impatient while completing it.
+By focusing on essential topics, the survey aims to encourage accurate responses without causing respondents to drop out.
+
+Stefanie Stantcheva also suggests the survey provide strong incentives for the respondents, in order to encourage respondents to complete the survey thoroughly and maximize participation.
+This could include offering a variety of possible rewards that appeal to a broad range of people, preventing not only attrition but also selection biases.
+
+If budget allows, offering cash or gifts as rewards could motivate the audience to participate, ensuring that the response rate remains high throughout the survey process.
+
+# Additional data details {#sec-appx-data}
 
@@
   theme_minimal() +
-  theme(legend.position = "bottom") +
+  theme(legend.position = "bottom",
+        legend.text = element_text(size = 5)
+  ) +
   coord_flip()
@@
 
-plot(model, "trace")
+plot(model, "trace") +
+    theme(
+          axis.text.x = element_text(size = 7),
+          axis.text.y = element_text(size = 5),
+          legend.title = element_text(size = 12),
+          legend.text = element_text(size = 10),
+          legend.position = "bottom",
+          strip.text = element_text(size = 6)
+    )
 ```

### 2024-12-01 scripts/03-clean_data.R
Updated script for data cleaning

@@ -1,7 +1,7 @@
 #### Preamble ####
 # Purpose: Cleans the raw data of Highrise Residential Fire Inspection Results
 # Author: Yunkai Gu
-# Date: 21 November 2024
+# Date: 1 December 2024
 # Contact: kylie.gu@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: Downloaded raw data from Open Data Toronto
@@ -46,10 +46,9 @@ cleaned_data <-
     violation = if_else(violations_item_number == 0, 0, 1)
   ) |>
   # Select and retain only the specified columns needed
-  select(address_name, enforcement_proceedings, property_type, 
-         inspections_opendate, inspections_closeddate, 
-         violations_item_number, date_num, violation)
+  select(property_type, inspections_opendate, inspections_closeddate, 
+         date_num, violation)
 
 
 #### Save data ####
-write_csv(cleaned_data, "data/02-analysis_data/fire_cleaned_data.csv")
+write_parquet(cleaned_data, "data/02-analysis_data/fire_cleaned_data.parquet")

### 2024-12-01 scripts/06-model_data.R
Updated script for modeling

@@ -1,7 +1,7 @@
 #### Preamble ####
 # Purpose: Construct Bayesian Model for fire inspection outcome
 # Author: Yunkai Gu
-# Date: 24 November 2024
+# Date: 28 November 2024
 # Contact: kylie.gu@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: Downloaded and cleaned data.
@@ -10,40 +10,41 @@
 
 #### Workspace setup ####
 library(tidyverse)
-library(janitor)
 library(lubridate)
-library(broom)
-library(modelsummary)
 library(rstanarm)
-library(splines)
+
 
 #### Read data ####
 cleaned_data <- read_csv("data/02-analysis_data/fire_cleaned_data.csv")
 
 
 ### Model data ####
+# Change 'property_type' to factor variables
 cleaned_data <- cleaned_data |>
   mutate(
-    address_name = factor(address_name),
     property_type = factor(property_type)
   )
 
+# Specify priors
 priors <- normal(0, 2.5, autoscale = TRUE)
 
+# Fit Bayesian model with date_num and property_type as fixed effect
 bayesian_model_1 <- stan_glm(
   formula = violation ~ date_num + property_type,
   data = cleaned_data,
   family = binomial(link = "logit"),
-  prior = priors,
-  prior_intercept = priors,
+  prior = normal(0, 2.5, autoscale = TRUE),
+  prior_intercept = normal(0, 2.5, autoscale = TRUE),
   seed = 123,
   cores = 4,
   adapt_delta = 0.95,
-  iter = 2000
+  iter = 4000
 )
 
+
+### Save the model ####
 saveRDS(
   bayesian_model_1,
-  file = "models/model_1.rds"
+  file = "models/violation_prediction_model.rds"
 )
 

### 2024-12-01 scripts/02-download_data.R
Updated scripts for downloading raw dataset

@@ -1,7 +1,7 @@
 #### Preamble ####
 # Purpose: Downloads and saves the data from Open Data Toronto (https://open.toronto.ca/dataset/highrise-residential-fire-inspection-results/)
 # Author: Yunkai Gu
-# Date: 21 November 2024
+# Date: 28 November 2024
 # Contact: kylie.gu@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: Installed `tidyverse` package
@@ -18,5 +18,3 @@ raw_data <- read_csv("https://ckan0.cf.opendata.inter.prod-toronto.ca/dataset/f8
 
 #### Save data ####
 write_csv(raw_data, "data/01-raw_data/fire_raw_data.csv") 
-
-         

### 2024-12-01 scripts/00-simulate_data.R
Updated script for simulation

@@ -1,52 +1,61 @@
 #### Preamble ####
-# Purpose: Simulates a dataset of Australian electoral divisions, including the 
-  #state and party that won each division.
-# Author: Rohan Alexander
-# Date: 26 September 2024
-# Contact: rohan.alexander@utoronto.ca
+# Purpose: Simulates a dataset of fire inspection outcomes which contains
+  # violation status by property type and inspection time interval
+# Author: Yunkai Gu
+# Date: 1 December 2024
+# Contact: kylie.gu@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: The `tidyverse` package must be installed
-# Any other information needed? Make sure you are in the `starter_folder` rproj
+# Pre-requisites: The `tidyverse` package must be installed.
+# Any other information needed? None
 
 
 #### Workspace setup ####
 library(tidyverse)
-set.seed(853)
+
+
+#### Simulation preparation ####
+# Set seed
+set.seed(123)
+
+# Set number of rows in simulation data
+n <- 13200
+
+# Property types
+property_type <- c(
+  "High Rise",
+  "Low Rise",
+  "Detension",
+  "Group Home",
+  "Group Home (VO)",
+  "Hospital",
+  "Hotel & Motel",
+  "Nursing Home",
+  "Residential Care",
+  "Rooming House"
+)
+
+# Violation indicator
+violation <- c(0,1)
 
 
 #### Simulate data ####
-# State names
-states <- c(
-  "New South Wales",
-  "Victoria",
-  "Queensland",
-  "South Australia",
-  "Western Australia",
-  "Tasmania",
-  "Northern Territory",
-  "Australian Capital Territory"
-)
-
-# Political parties
-parties <- c("Labor", "Liberal", "Greens", "National", "Other")
-
-# Create a dataset by randomly assigning states and parties to divisions
-analysis_data <- tibble(
-  division = paste("Division", 1:151),  # Add "Division" to make it a character
-  state = sample(
-    states,
-    size = 151,
-    replace = TRUE,
-    prob = c(0.25, 0.25, 0.15, 0.1, 0.1, 0.1, 0.025, 0.025) # Rough state population distribution
-  ),
-  party = sample(
-    parties,
-    size = 151,
-    replace = TRUE,
-    prob = c(0.40, 0.40, 0.05, 0.1, 0.05) # Rough party distribution
-  )
+simulated_data <- tibble(
+  #Randomly select from a set of property types
+  property_type = sample(property_type, n, replace = TRUE), 
[…]

### 2024-12-01 scripts/01-test_simulated_data.R
Updated script for testing the simulated dataset

@@ -1,20 +1,25 @@
 #### Preamble ####
-# Purpose: Tests the structure and validity of the simulated Australian 
-  #electoral divisions dataset.
-# Author: Rohan Alexander
-# Date: 26 September 2024
-# Contact: rohan.alexander@utoronto.ca
+# Purpose: Tests the structure and validity of the simulated fire inspection
+  #outcome dataset.
+# Author: Yunkai Gu
+# Date: 1 December 2024
+# Contact: kylie.gu@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: 
   # - The `tidyverse` package must be installed and loaded
   # - 00-simulate_data.R must have been run
-# Any other information needed? Make sure you are in the `starter_folder` rproj
+# Any other information needed? Make sure you are in the `Toronto_Fire_Inspection` rproj
 
 
 #### Workspace setup ####
 library(tidyverse)
 
-analysis_data <- read_csv("data/00-simulated_data/simulated_data.csv")
+
+# Read the dataset
+analysis_data <- read_csv("data/00-simulated_data/fire_simulated_data.csv")
+
+
+#### Test data ####
 
 # Test if the data was successfully loaded
 if (exists("analysis_data")) {
@@ -23,48 +28,72 @@ if (exists("analysis_data")) {
   stop("Test Failed: The dataset could not be loaded.")
 }
 
-
-#### Test data ####
-
-# Check if the dataset has 151 rows
-if (nrow(analysis_data) == 151) {
-  message("Test Passed: The dataset has 151 rows.")
+# Check if the dataset has 13193 rows
+if (nrow(analysis_data) == 13193) {
+  message("Test Passed: The dataset has 13193 rows.")
 } else {
-  stop("Test Failed: The dataset does not have 151 rows.")
+  stop("Test Failed: The dataset does not have 13193 rows.")
 }
 
-# Check if the dataset has 3 columns
-if (ncol(analysis_data) == 3) {
-  message("Test Passed: The dataset has 3 columns.")
+# Check if the dataset has 5 columns
+if (ncol(analysis_data) == 5) {
+  message("Test Passed: The dataset has 5 columns.")
 } else {
-  stop("Test Failed: The dataset does not have 3 columns.")
+  stop("Test Failed: The dataset does not have 5 columns.")
 }
 
-# Check if all values in the 'division' column are unique
-if (n_distinct(analysis_data$division) == nrow(analysis_data)) {
-  message("Test Passed: All values in 'division' are unique.")
[…]

### 2024-12-01 scripts/04-test_analysis_data.R
Updated script for testing cleaned dataset

@@ -1,69 +1,111 @@
 #### Preamble ####
-# Purpose: Tests... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 26 September 2024 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Tests the structure and validity of the fire inspection outcome 
+  # dataset after cleaning.
+# Author: Yunkai Gu
+# Date: 1 December 2024
+# Contact: kylie.gu@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: 
+# - The `tidyverse` package must be installed and loaded
+# - 02-download_data.R and 03-clean_data.R must have been run
+# Any other information needed? Make sure you are in the `Toronto_Fire_Inspection` rproj
 
 
 #### Workspace setup ####
 library(tidyverse)
-library(testthat)
 
-data <- read_csv("data/02-analysis_data/analysis_data.csv")
+
+# Read the dataset
+analysis_data <- read_parquet("data/02-analysis_data/fire_cleaned_data.parquet")
 
 
 #### Test data ####
-# Test that the dataset has 151 rows - there are 151 divisions in Australia
-test_that("dataset has 151 rows", {
-  expect_equal(nrow(analysis_data), 151)
-})
 
-# Test that the dataset has 3 columns
-test_that("dataset has 3 columns", {
-  expect_equal(ncol(analysis_data), 3)
-})
+# Test if the data was successfully loaded
+if (exists("analysis_data")) {
+  message("Test Passed: The dataset was successfully loaded.")
+} else {
+  stop("Test Failed: The dataset could not be loaded.")
+}
 
-# Test that the 'division' column is character type
-test_that("'division' is character", {
-  expect_type(analysis_data$division, "character")
-})
+# Check if the dataset has 13193 rows
+if (nrow(analysis_data) == 13193) {
+  message("Test Passed: The dataset has 13193 rows.")
+} else {
+  stop("Test Failed: The dataset does not have 13193 rows.")
+}
 
-# Test that the 'party' column is character type
-test_that("'party' is character", {
-  expect_type(analysis_data$party, "character")
-})
+# Check if the dataset has 5 columns
+if (ncol(analysis_data) == 5) {
+  message("Test Passed: The dataset has 5 columns.")
[…]

### 2024-12-01 scripts/00-simulate_data.R
Updated script for simulating data

@@ -5,7 +5,7 @@
 # Date: 1 December 2024
 # Contact: kylie.gu@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: The `tidyverse` package must be installed.
+# Pre-requisites: The `tidyverse` package must be installed and loaded
 # Any other information needed? None
 
 
@@ -18,13 +18,13 @@ library(tidyverse)
 set.seed(123)
 
 # Set number of rows in simulation data
-n <- 13200
+n <- 13193
 
 # Property types
 property_type <- c(
   "High Rise",
   "Low Rise",
-  "Detension",
+  "Detention",
   "Group Home",
   "Group Home (VO)",
   "Hospital",
@@ -42,16 +42,16 @@ violation <- c(0,1)
 simulated_data <- tibble(
   #Randomly select from a set of property types
   property_type = sample(property_type, n, replace = TRUE), 
-  #Randomly selected dates from 2019-07 to 2024-11 as open date
-  inspections_opendate = sample(seq(as.Date("2019-07-01"), 
-                                    as.Date("2024-11-30"), by = "day"), 
+  #Randomly selected dates from 2019-07-09 to 2024-11-20 as open date
+  inspections_opendate = sample(seq(as.Date("2019-07-09"), 
+                                    as.Date("2024-11-20"), by = "day"), 
                                 n, replace = TRUE),
-  #Randomly selected dates from 2024-01 to 2024-11 as closed date
-  inspections_closeddate = sample(seq(as.Date("2024-01-01"), 
-                                    as.Date("2024-11-30"), by = "day"), 
+  #Randomly selected dates from 2024-01-02 to 2024-11-28 as closed date
+  inspections_closeddate = sample(seq(as.Date("2024-01-02"), 
+                                    as.Date("2024-11-28"), by = "day"), 
                                 n, replace = TRUE),
-  # Randomly select integers from 0 to 1700 
-  date_num = sample(0:1700, n, replace = TRUE),
+  # Randomly select integers from 0 to 1679
+  date_num = sample(0:1679, n, replace = TRUE),
   #Randomly select from 1 and 0 for violation indicator
   violation = sample(violation, n, replace = TRUE)
 )

### 2024-12-01 scripts/01-test_simulated_data.R
Updated script for testing simulated dataset

@@ -45,7 +45,7 @@ if (ncol(analysis_data) == 5) {
 # Check if the 'property_type' column contains only valid property types
 valid_types <- c("High Rise",
                   "Low Rise",
-                  "Detension",
+                  "Detention",
                   "Group Home",
                   "Group Home (VO)",
                   "Hospital",

### 2024-12-01 scripts/00-simulate_data.R
Updated script for simulating data

@@ -6,7 +6,7 @@
 # Contact: kylie.gu@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: The `tidyverse` package must be installed and loaded
-# Any other information needed? None
+# Any other information needed? Make sure you are in the `Toronto_Fire_Inspection` rproj
 
 
 #### Workspace setup ####

### 2024-12-01 scripts/02-download_data.R
Updated script for downloading raw dataset

@@ -4,8 +4,8 @@
 # Date: 28 November 2024
 # Contact: kylie.gu@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: Installed `tidyverse` package
-# Any other information needed? None
+# Pre-requisites: The `tidyverse` package must be installed and loaded
+# Any other information needed? Make sure you are in the `Toronto_Fire_Inspection` rproj
 
 
 #### Workspace setup ####

### 2024-12-01 scripts/03-clean_data.R
Updated script for cleaning dataset

@@ -4,8 +4,10 @@
 # Date: 1 December 2024
 # Contact: kylie.gu@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: Downloaded raw data from Open Data Toronto
-# Any other information needed? None
+# Pre-requisites:
+# - The `tidyverse` `dplyr` `lubridate` package must be installed and loaded
+# - 02-download_data.R must have been run
+# Any other information needed? Make sure you are in the `Toronto_Fire_Inspection` rproj
 
 #### Workspace setup ####
 library(tidyverse)

### 2024-12-01 scripts/06-model_data.R
Updated scripts for modeling

@@ -4,8 +4,10 @@
 # Date: 28 November 2024
 # Contact: kylie.gu@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: Downloaded and cleaned data.
-# Any other information needed? None
+# Pre-requisites:
+# - The `tidyverse` `lubridate` `rstanarm` package must be installed and loaded
+# - 02-download_data.R and 03-clean_data.R must have been run
+# Any other information needed? Make sure you are in the `Toronto_Fire_Inspection` rproj
 
 
 #### Workspace setup ####

### 2024-12-02 paper/paper.qmd
Updated sampling and survey section in appendix

@@
 
+## Sampling Approach
+
+### Target Population
+
+Target population refers to the population of the survey's interest.
+The target population for this fire safety feedback survey includes all residents of residential buildings in Toronto that have undergone fire safety inspections within the last 12 months, varying in property type and geographic location within the city.
+
+This diverse target population ensures a broad range of perspectives on fire safety measures, reflecting various living conditions across different areas of the city.
+
+### Sampling Frame
+
+The sampling frame or pool of potential respondents represents all the people in the population potentially to be sampled and invited to the survey [@howtorunsurveys].
+In this research, the sampling frame will be based on a list of properties from inspection records.
+The survey will be distributed by contacting the building management or tenant associations of those properties, who will then send the surveys to the residents for completion.
+
+This process will be carried out in full compliance with privacy laws to ensure that residents' personal information is protected and that their participation remains confidential.
+
+### Stratified Random Sampling
+
+To ensure the survey on fire safety compliance gathers reliable and representative data, a stratified random sampling method will be employed.
+The sampling approach follows the guidelines in "Survey Methodology" [@surveymethodology].
+
+This approach divides the frame of population elements into meaningful subgroups, or "strata", which are "mutually exclusive groups of elements on a sampling frame" [@surveymethodology].
+Then, separate samples are drawn from each stratum, using randomization techniques (e.g.
+random number generators) to select participants within each stratum.
+
+The strata for this study will include the following categories:
+
+- Region: The geographic address of the property, ensuring representation from different areas within Toronto.
+
+- Property Type: The occupancy type of the property, which includes various categories such as high-rise, low-rise, detention, group homes, group homes for vulnerable individuals (VO), hospitals, hotels & motels, nursing homes, residential care, and rooming houses.
+
+This study plans to mount a survey collecting feedback of fire safety inspection of properties and expect that the results vary across different property types and regions in Toronto.
+Therefore, the strata will be defined based on key characteristics relevant to building types and location information.
+
+### Planned Sample and Sample Size
+
+The planned or target sample is all the people that ideally to be included to complete the survey [@howtorunsurveys].
+
+The sample size should be determined by both considering to achieve statistical significance and to meet resource constraints.
+After obtaining information about sample frame size, or the total number of residents across all strata, the proportion of the planned sample size allocated to each stratum should match the proportion of that stratum in the overall target population.
+
+This approach ensures proportional representation from each stratum, reflecting the diversity of the population and improving the generalizability of the survey results.
+By maintaining this balance, the sample could provide a complete overview while meeting the constraints of available resources.
+
+### Potential Errors
+
+- Coverage Error
+
+Coverage error is the difference between the potential pool of respondents and the target population [@howtorunsurveys].
+In other words, the sampling frame does not fully represent the target population.
+
+In this research, the surveys will be distributed to residents using online Google Forms.
+However, since the recruitment relies on digital methods, there is a potential risk of underrepresentation for properties in regions or with property types where a majority of residents lack internet access or digital literacy.
+This could result in skewed data, with certain populations being less likely to participate.
+
+Additionally, since the sampling frame is based solely on official building management contact information, residents in informal or unregistered housing arrangements may be excluded from the survey.
+This limitation could further affect the representativeness of the sample, as it excludes individuals living in non-official housing setups who may also be affected by fire safety measures.
+
+- Sampling Error
+
+Sampling error refers to the difference between the planned sample and the sampling frame, that is, "the fact that you are drawing only a sample from the full sampling frame" [@howtorunsurveys].
+
+In this research, despite randomization, it may still be possible that the selected individuals within a stratum do not represent the overall stratum accurately.
+This could occur due to certain individuals being overrepresented or underrepresented by chance.
+As a result, while randomization aims to minimize bias, sampling error could still influence the accuracy and precision of the findings.
+
+- Non-response Error
+
+Non-response error refers to the differences between the target sample and the actual sample [@howtorunsurveys].
+
+In this research, the error could arise due to the residents not receiving or seeing the invitation of the survey.
+Since the surveys are distributed by building management or tenant associations through online platforms such as emails, there is a risk that the survey invitations may be overlooked or filtered into spam folders.
+Email-based distribution depends on residents regularly checking their inboxes, and not every resident has such habit.
+If the email is sent from an unfamiliar address or lacks clear identification, residents might dismiss it as junk or advertising mail, and ignore it entirely.
+Furthermore, some email systems automatically filter certain messages into spam folders, reducing the visibility of the survey and limiting participation.
+
+Additionally, residents may ignore the survey invitation, potentially due to the lack of immediate rewards or incentives for participation.
+Without clear incentives, such as gift cards or other tangible rewards, residents may not feel motivated to take the time to complete the survey.
+This lack of incentive could result in lower response rates, particularly among residents who do not understand the survey’s importance.
+As a result, the data collected might not fully capture the perspectives of all residents, leading to potential bias in the findings.
+
+More detailed discussion and potential solutions would be discussed in @sec-survey-bias.
+
 ## Survey
 
-This survey will be conducted using Google Forms, which is an effective platform for data collection. The survey can be accessed by the link, [Google Form Survey].
+This survey will be conducted using Google Forms, which is an effective platform for data collection. It can be accessed by this link: [Google Form Survey](https://forms.gle/SMaPsDLVG1v33Ecy9).
 
@@
 
-### Survey Design Considerations: Biases and Solutions
+### Survey Design Considerations: Biases and Solutions {#sec-survey-bias}
 

### 2024-12-02 paper/paper.qmd
Updated introduction and abstract

@@
 ---
-title: "Fire Safety Regulation Violations in Toronto: Analysis by Property Type and Inspection Duration for Inspections Closed in 2024"
-subtitle: "My subtitle if needed"
+title: "Fire Safety Regulation Violations in Toronto Residential Properties: Analysis by Property Type and Inspection Duration"
+subtitle: "Most properties would have a high probability of violation, whereeas high-rise buildings, rooming houses, and group homes have the highest risk"
 author: 
@@
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "This paper analyzes fire safety regulation violations in residential properties across Toronto, predicting the likelihood of violations based on the inspection duration and property type.
+By using a Bayesian logistic regression model, the study finds that property type plays a significant role in predicting violations, with high-rise buildings, rooming houses, and group homes at higher risk, and predicts with high confidence that most properties in the city would have a high probability of being observed to have a violation of fire safety regulations.
+These findings are important for improving fire safety protocols, as they suggest that targeting inspections towards high-risk property types could lead to more effective resource allocation and better safety outcomes.
+Findings in the study would motivate targeted inspections and interventions concentrated on properties that present the greatest risk, enhancing the effectiveness of fire safety efforts and helping to reduce potential fire accidents more efficiently."
 format: pdf
@@
 
-Overview paragraph
-
-Estimand paragraph
-
-Results paragraph
-
-Why it matters paragraph
-
-Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....
+In recent years, fire safety inspections in residential buildings have gained increasing attention from the public due to their role in ensuring the safety of residents and reducing potential dangers caused by fire-related accidents.
+Toronto Fire Services (TFS) fire prevention and enforcement strategies, which are guided by the Fire Protection and Prevention Act, 1997 (FPPA) and regulations under it (such as Ontario Fire Code), aim to increase public safety and awareness [@fire_info].
+In order to achieve this goal, TFS have been conducting inspections across a wide range of residential properties within the entire city to ensure properties' compliance with fire safety regulations.
+However, despite these efforts, there remains a limited understanding of the factors influencing the likelihood of fire safety violations across different property types and inspection durations.
+As a result, targeted interventions have not yet been effectively implemented for high-risk buildings.
+Therefore, this paper aims to analyze the impact of both inspection time interval and property type on the likelihood of violations in fire safety checks.
+By doing so, a model that provides predictions of violations based on specific features of the properties and inspection characteristics could be developed, improving TFS's ability to prioritize resources and focus on properties that require the most attention.
+
+The focus of this study is to investigate how different property types and inspection time intervals contribute to fire safety violations in Toronto, and this paper uses Bayesian logistics model to conduct predictions.
+The predictor variables examined include the time interval of the inspection process, and the type of property being inspected.
+By exploring these factors, the paper aims to predict the likelihood of violations, conducting predictions of which property types are at higher risk for violations and how inspection duration might influence these outcomes.
+The estimand would be described in detail in @sec-estimand.
+
+As included at the end of the analysis, the model predicts with high confidence that most properties would have a high probability of being observed to have a violation of fire safety regulations.
+Such prediction by the model is confident, highlighting the utility of the model in helping to conduct targeted inspections and interventions where they are most needed.
+Moreover, the analysis further highlights that different property types have varying impacts on the likelihood of fire safety violations.
+The model confidently predicts that among ten property types inspected, "High Rise," "Rooming House," and "Group Home" are more likely to have violations.
+As a result, these property types should receive more targeted inspections and interventions.
+Along with "Low Rise" and "Hotel & Motel," these property types show strong evidence of being associated with higher risks of violations.
+In contrast, the model indicates that "Nursing Home" has the lowest risk of violations among ten property types inspected and some uncertainty exist in the strength of this predicted relationship.
+
+This research contributes to improving fire safety facilities in residential buildings in Toronto by providing empirical evidence and statistical predictions that supports the allocation of inspection resources based on both the property type and inspection time interval.
+By highlighting which property types with how long inspection duration are most at risk for fire safety violations, the findings offer a valuable approach to prioritizing inspections and interventions.
+The results of the study have broader implications for fire safety policy, as they could be used to improve future regulatory practices and resource allocation strategies.
+By ensuring that inspection resources are concentrated on properties that present the greatest risk, this study would enhance the effectiveness of fire safety efforts, and help to reduce potential fire accidents more efficiently.
+
+The remainder of this paper is structured as follows:
+
+@sec-data introduces the overview of the data (@sec-data-overview) and measurement (@sec-data-measure), as well as explanations, descriptions, table and graph summaries of outcome (@sec-data-outcome) and predictor variables (@sec-data-predictor) of the study.
+@sec-model explains the modeling process in detail, including procedure of model set-up (@sec-model-set), model assumptions and limitations (@sec-model-assume), and model justification (@sec-model-justify).
+Then, @sec-result presents the model outcome and results by tables and plots, and @sec-discussion discusses the study in a broader context.
+
+Appendix includes three parts:[Appendix -@sec-appx-survey] describes detailed idealized sampling methodology and survey designed for residents to collect fire safety feedback; [Appendix -@sec-appx-data] provides additional data details; [Appendix -@sec-model-details] presents additional details during modeling process, including posterior predictive check [Appendix -@sec-ppc], comparison between posterior and prior distributions [Appendix -@sec-pvp], and diagnostics [Appendix -@sec-diagnostics].
+
+## Estimand {#sec-estimand}
+
+The estimand in this paper is the probability of a fire safety violation occurring in residential properties in Toronto, based on two primary factors: inspection duration (measured as the time interval between the start and end of the inspection process) and property type (such as high-rise, low-rise, group home, etc., a total of ten types).
+The goal of the analysis is to evaluate how these factors influence the likelihood of a violation being detected during fire safety inspections.
+
+Specifically, the estimand is modeled as the probability that a property will fail the fire safety inspection (i.e., a violation is found) based on these two predictors.
+The response variable is binary: a violation is either observed (1) or not observed (0).
+This probability is expressed as a function of the inspection time interval and the property type, with the logistic regression model used to predict the outcome, estimating the log-odds of a violation for different values of these predictors.
+
+The estimand, therefore, directly addresses the question: "What is the likelihood of a violation being observed during the inspection process for a given property, based on its property type and the duration of the inspection?" By understanding the prediction results of the study, identifying which properties are at higher risk of violations would be possible, and the conclusions could be used for guiding TFS to conduct more targeted inspections and interventions to residential properties.
 
@@
 
-## Overview
+## Overview {#sec-data-overview}
 
@@
 
-## Measurement {#sec-measure}
+## Measurement {#sec-data-measure}
 
@@
 
-## Outcome Variable
+## Outcome Variable {#sec-data-outcome}
 
@@
 
-## Predictor Variables
+## Predictor Variables {#sec-data-predictor}
 
@@
 
-# Model
+# Model {#sec-model}
 
@@
 
-## Model set-up
+## Model set-up {#sec-model-set}
 
@@
 
-## Model Assumptions and Limitations
+## Model Assumptions and Limitations {#sec-model-assume}
 
@@
 
-## Model Justification
+## Model Justification {#sec-model-justify}
 
@@
 
-# Results
+# Results {#sec-result}
 
@@
 
-On the other hand, a few parameters have 95% confidence interval including 0, such as property types of "Group Home", "Group Home (VO)", "Nursing Home".
+On the other hand, two parameters have 95% confidence interval including 0, which are property types of "Group Home (VO)" and "Nursing Home".
 This represents that the effect of the variables on violations is not statistically significant, and the relationship is uncertain.
@@
 
-# Discussion
+### Conclusion
+
+The results of the Bayesian logistic regression model indicates that the duration of the inspection has a negligible impact on the likelihood of violations, whereas the predictor variable of property type plays a more significant role in determining violations.
+The model predicts with high confidence that most properties would have a high probability of being observed to have a violation of fire safety regulations, shown by the distribution of predicted probabilities.
+Such prediction by the model in identifying properties at high risk of violations is confident, highlighting the utility of the model in helping to conduct targeting inspections and interventions where they are most needed.
+
+The analysis further highlights that property types have varying impacts on the likelihood of fire safety violations.
+Among the property types, "High Rise", "Rooming House" and "Group Home" have the highest risk of violations compared to the reference property type, shown by the large, positive coefficients.
+These property types are followed by "Low Rise" and "Hotel & Motel," which also show relatively high risks of violations.
+For these five property types, there is strong evidence supporting their relationship with the likelihood of violations, as their 95% confidence intervals do not include zero, suggesting a statistically significant impact.
+
+On the other hand, "Nursing Home" shows the smallest coefficient with confidence interval including zero, suggesting a relatively lowest risk of violations and some uncertainty regarding the strength of the relationship.
+Despite this, "Nursing Home" still demonstrates a positive, though weaker, risk of violations compared to other property types.
+
+# Discussion {#sec-discussion}
 
@@
 
-## Posterior Predictive Check
+## Posterior Predictive Check {#sec-ppc}
 
@@
 
-## Posterior vs Prior
+## Posterior vs Prior {#sec-pvp}
 
@@
 
-## Diagnostics
+## Diagnostics {#sec-diagnostics}
 

### 2024-12-03 paper/paper.qmd
Updated discussion section in paper

@@
 
-### Conclusion
+## Conclusion
 
@@
 
-## What is done in this paper?
-
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
-
-## What is something that we learn about the world?
-
-Please don't use these as sub-heading labels - change them to be what your point actually is.
-
-## What is another thing that we learn about the world?
-
-## Weaknesses and next steps
-
-Firstly, the limitations in the process of measurement of the original dataset should be considered. Specifically, the limitations include:
+## Overview of the Paper
+
+This paper investigates the factors that influence fire safety violations in residential buildings in Toronto, with a particular focus on the role of property type and inspection duration.
+The central aim is to predict the likelihood of violations, conducting predictions of which property types are at higher risk for violations and how inspection duration might influence these outcomes.
+The paper uses a Bayesian logistic regression model to analyze data from properties that underwent fire safety inspections by Toronto Fire Services (TFS).
+The raw dataset is obtained from Open Data Toronto, and a data cleaning process is performed to retain only inspection cases with a closed date within 2024, ensuring that the data reflects the most recent developments and provides an up-to-date basis for analysis.
+By focusing on the inspection outcomes of the properties where the inspection process was completed in 2024, the study uses a binary outcome variable to indicate whether a violation was observed (1) or not observed (0), facilitating a clear distinction between properties that violated fire safety regulations and those that did not.
+
+The analysis includes two main predictor variables: the inspection time interval and property type.
+The inspection time interval refers to the duration between the start and end date of the inspection, and property type includes ten categories, such as high-rise buildings, low-rise buildings, group homes, and others.
+These two variables were selected based on their potential to influence the outcome of fire safety inspections.
+The inspection duration was expected to be a relevant predictor since longer inspections might allow for more thorough checks, potentially leading to more cases with violations being detected.
+Similarly, different property types were assumed to have varying levels of probability of violating fire safety regulations, as the unique features and characteristics of the occupancy types may lead to more or less additional safety concerns.
+
+The study employs a Bayesian logistic regression model to analyze the data, allowing for the prediction of the likelihood of violations and considering uncertainty around the estimates at the same time.
+The results of the model are stated as follows: the model predicts with high confidence that most properties would have a high probability of being observed to have a violation of fire safety regulations; Different property types have varying impacts on the likelihood of fire safety violations; Duration of the inspection has a negligible impact on the likelihood of violations; Among ten property types inspected, "High Rise," "Rooming House," and "Group Home" are more likely to have violations and therefore should receive more targeted inspections and interventions.
+
+Overall, the paper identifies the role of property type as a key factor influencing fire safety regulation violation status in Toronto.
+The findings of the study could then be used to motivate targeted inspections and interventions, allowing fire prevention resources to be concentrated on properties that present the highest risk.
+Prioritizing high-risk buildings enhances the effectiveness of fire safety efforts, and helps to reduce potential fire accidents more efficiently.
+
+## Varying Possibility of Violation for Different Property Types
+
+One of the key lessons from this study is that property type plays an important role in determining the likelihood of fire safety violations.
+The findings show that property types of high-rise buildings, group homes, and rooming houses have a significantly higher possibility of violations compared to other types.
+This finding highlights the importance of property characteristics in influencing fire safety outcomes, rather than assuming all properties face the same risks.
+
+In the real world, such result could assist Toronto Fire Services and other fire safety authorities in prioritizing their efforts and allocating the fire prevention resources more efficiently.
+Properties with higher risk of violation would require more frequent, careful and thorough inspections, as well as more targeted fire safety interventions.
+For instance, high-rise buildings typically have more complex layouts and higher occupancy, presenting unique fire safety challenges.
+One example of such difficulties is that extra actions would be needed to ensure that fire safety measures are effective across multiple floors.
+Authorities could focus on addressing these challenges by conducting more frequent maintenance of fire safety equipment, such as alarms, sprinklers, and fire exits, testing that they are functioning properly throughout the building, and implementing enhanced systems preventing fire accidents.
+
+By focusing on high-risk property types, Toronto Fire Services could allocate resources more effectively, ensuring that inspections are concentrated in areas where they are most needed.
+This would help protect the residents living in those properties from fire-related dangers.
+Additionally, this targeted approach would motivate the city to consider fire safety regulations targeted specifically to these property types.
+Furthermore, there is potential to arise the residents' awareness of fire safety issues, encouraging greater public attention to fire prevention.
+This heightened awareness could lead to more voluntary fire safety practices, both within buildings and in the community, reducing the risk of fire-related incidents across Toronto.
+
+## Limited Role of Inspection Duration in Predicting Violations
+
+Another key learning from this paper is that inspection duration — the time interval between the start date and the closed date of the inspection — does not significantly affect the likelihood of fire safety violations found in properties.
+While it is expected that longer inspections lead to more thorough checks and thus a higher probability of identifying violations, the findings of this study challenge this idea.
+The study suggests that the duration of the inspection has a negligible impact on the detection of violations.
+
+In practical terms, this finding is valuable for fire safety management and resource allocation.
+Toronto Fire Services may reconsider the emphasis placed on inspection duration.
+If longer inspections are not significantly improving the detection of violations, resources could be better spent on other aspects of the inspection process, such as using advanced fire safety technologies, improving inspector training, or focusing on properties with higher violation risks.
+This could make the inspection process be more cost-effective by reducing the time spent on inspections, while still maintaining the quality of fire safety prevention procedure.
+
+As stated before, the study’s findings further suggest that the key to effective fire safety inspections lies in targeting high-risk properties rather than increasing inspection time.
+Fire safety inspections could be made more efficient by focusing on properties with higher violation risks, based on their property type or past inspection records.
+This targeted approach could lead to better outcomes, encouraging fire safety authorities to shift their focus from inspection duration to more strategic inspection methodologies.
+
+## Weaknesses and Limitations
+
+The limitations in the process of measurement of the original dataset should be considered. Specifically, the limitations include:
 
@@
 
-Various interpretations of the guidelines and different decision-making procedures made by the inspectors based on specific situations could impact the outcome of the inspection.
-Since the examinations have been thoroughly completed by human, the assessments could differ depending on the inspectors' focus and perspectives on certain regulations, influencing the observations recorded, even with clear rules.
+Various interpretations of the guidelines and different decision-making procedures employed by the inspectors based on specific situations could impact the outcome of the inspection.
+The inspectors' focus during an inspection may vary depending on their experience, training, and individual judgment.
+Even though the examinations are conducted following clear rules, the outcomes of assessments could differ based on the inspectors' focus on certain regulations.
+As a result, the observations recorded during inspections might vary, introducing potential inconsistencies in how violations are identified.
+This variability could lead to differences in the recorded outcomes of inspections, impacting the reliability of the data.
 
@@
 
-The dataset does not capture all fire safety-related phenomena in Toronto, as it only contains the properties that have been inspected by the Inspectors from TFS.
-The properties that are not included in the list fail to provide any information, which would make the dataset not representative enough to conclude the situations of fire safety checks for the whole city.
+The dataset does not capture all fire safety-related phenomena in Toronto, as it only contains the properties that have been inspected by the Inspectors from Toronto Fire Services.
+Properties that have not been inspected are not included in the dataset, meaning that there is no information available about their fire safety violation status.
+This limitation means that the dataset may not be fully representative of the overall fire safety situation across the city.
+Without data from properties that were not inspected, it is difficult to draw generalized conclusions about fire safety checks for the entire city, as the sample may be biased towards properties that have undergone inspection.
 
 Moreover, even for the properties that have been inspected by TFS, not all cases are recorded in the dataset.
-The raw dataset only includes 'closed' cases, which are specific cases where the inspection process has ended, and does not account for cases currently under review or in progress.
+The raw dataset only includes 'closed' cases, which are specific cases where the inspection process has ended.
+It does not account for cases currently under inspection or in progress, potentially leading to an incomplete picture of the fire safety status in Toronto.
 
 In other words, the properties whose initial observations have been made but further investigation or corrective actions are required, are excluded from the dataset.
-Therefore, the dataset does not represent the full scope of fire safety checks at any given time.
-The active cases would be neglected in analysis procedure, providing limited insights to identify fire safety concerns in real-time.
+Any ongoing cases, particularly those that are in the early stages of investigation, are not included.
+This could potentially lead to selection bias and skew the results.
+Therefore, the dataset fails to represent the full scope of fire safety checks at any given time.
+The active cases would be neglected in the analysis, providing limited basis to identify fire safety concerns in real-time.
+
+## Future Steps
+
+To further improve fire safety prevention and ensure more effective inspections, potential future research and action should be considered.
+
+One key step for future research is try to include ongoing inspections and active enforcement cases in the analysis.
+The current study only took closed inspection cases into consideration, excluding properties still under review or those requiring further enforcement.
+This potentially introduces a selection bias.
+By including ongoing inspections and active cases, future studies could provide a more generalized view of fire safety violations for properties in Toronto, and further offer evaluation of how violations evolve over time.
+Potentially, examining the dates of inspections and corresponding outcomes could help understand whether certain time periods lead to higher rates of violation of fire safety regulations in residential properties.
+
+While property type and inspection duration were the primary focus of this study, other factors which may contribute to the likelihood of fire safety violations should also be taken into consideration.
+Future research should include additional aspects and variables, such as building age, maintenance history, fire safety training for residents, and even fire department resources.
+For instance, older buildings or those with a history of poor maintenance may have larger possibility to be detected for violations.
+Another example is regional differences: Properties in certain areas of the city may face different fire safety challenges due to their geographic location or local regulations.
+Understanding these additional factors could help create a more complete model to predict fire safety violations and lead to more targeted inspection strategies.
+
+After the inspection and enforcement process ends, Toronto Fire Services could also check the outcomes of fire safety inspections to obtain a general overview of the fire prevention status in the city.
+Including resident feedback through surveys or interviews could provide valuable insights into the effectiveness of fire safety inspections and regulations from the perspective of the people directly affected by these policies.
+Detailed idealized methodology would be further discussed in [Appendix -@sec-appx-survey].
+Moreover, residents' awareness of fire safety could also be considered as an additional factor to be included in the model.
+Future research could examine how residents’ knowledge of fire safety regulations, their adherence to safety practices, and their willingness to report violations impact the likelihood of violations.
+
+In conclusion, while this paper offers predictions and analysis of fire safety violations in Toronto, there are still many questions left to answer.
+By expanding the scope of the analysis by including additional variables, or possibly distributing surveys to the residents, future research could provide a more complete picture of fire safety status in the residential properties in the city.
+This will help fire safety authorities develop more targeted, efficient, and sustainable strategies for reducing violations, and ensuring the safety of residents.
 
@@
 
-# Surveys, Sampling, and Observational Data
+# Surveys, Sampling, and Observational Data {#sec-appx-survey}
 

### 2024-12-03 scripts/03-clean_data.R
Updated script for dataset cleaning

@@ -13,6 +13,8 @@
 library(tidyverse)
 library(dplyr)
 library(lubridate)
+library(janitor)
+library(arrow)
 
 
 #### Clean data ####

### 2024-12-03 paper/paper.qmd
Updated addtional model details in paper

@@
 title: "Fire Safety Regulation Violations in Toronto Residential Properties: Analysis by Property Type and Inspection Duration"
-subtitle: "Most properties would have a high probability of violation, whereeas high-rise buildings, rooming houses, and group homes have the highest risk"
+subtitle: "High Probability of Violations Across Most Properties, with High-Rise Buildings, Rooming Houses, and Group Homes Exhibiting the Highest Risk"
 author: 
@@
 date-format: long
-abstract: "This paper analyzes fire safety regulation violations in residential properties across Toronto, predicting the likelihood of violations based on the inspection duration and property type.
+abstract: "This paper analyzes fire safety regulation violations in residential properties across Toronto, predicting the likelihood of violations based on the inspection duration and property type, using data from fire safety inspections ended during 2024.
 By using a Bayesian logistic regression model, the study finds that property type plays a significant role in predicting violations, with high-rise buildings, rooming houses, and group homes at higher risk, and predicts with high confidence that most properties in the city would have a high probability of being observed to have a violation of fire safety regulations.
@@
 library(lubridate)
-library(broom)
 library(modelsummary)
 library(rstanarm)
-library(splines)
 library(ggplot2)
@@
 library(RColorBrewer)
+library(broom)
 library(broom.mixed)
@@
 # Read the cleaned data
-cleaned_data <- read_csv(
-  file = here::here("data/02-analysis_data/fire_cleaned_data.csv")
+cleaned_data <- read_parquet(
+  file = here::here("data/02-analysis_data/fire_cleaned_data.parquet")
   )
-data <- read_csv(
-  file = here::here("data/02-analysis_data/fire_cleaned_data.csv")
-  )
-
 ```
@@
 
-More detailed data cleaning process is included in [Appendix -@sec-appx-data].
+@tbl-overview presents several sample lines of the cleaned dataset. More detailed data cleaning process is included in [Appendix -@sec-appx-data].
+
+```{r}
+#| echo: false
+#| eval: true
+#| label: tbl-overview
+#| tbl-cap: "Preview of the Cleaned Dataset"
+#| warning: false
+
+cleaned_data |>
+  head() |>
+  kable(format = "simple")
+```
 
 The analyses presented in this paper were conducted using R programming language [@citeR].
-The `tidyverse` packages [@citetidyverse] were used in the process of data simulation, testing beforehand.
-After the original raw data was downloaded by using `tidyverse` package [@citetidyverse], data cleaning process was done by using `tidyverse` package [@citetidyverse], `lubridate` package [@citelubridate], and `arrow` package [@citearrow].
-We use `testthat` package [@citetest] to develop the test for structure and format of simulation and analysis data.
+The `tidyverse` packages [@citetidyverse] were used in the process of data simulation, testing and downloading.
+After the original raw data was successfully downloaded, data cleaning process was done by using `tidyverse` package [@citetidyverse], `lubridate` package [@citelubridate], `janitor` package [@citejanitor] and `dplyr` package [@citedplyr].
+The analysis dataset after cleaning is saved as a parquet file using `arrow` package [@citearrow].
 
@@
 The model results were then presented by both the tables and graphs.
-Tables were made with `modelsummary` [@citemodelsummary] package, `broom.mixed` [@citebroom] package, `dplyr` [@citedplyr] package and `knitr` package.
-Graphs were made with `ggplot2` package [@citeggplot] and `RColorBrewer` package [@citercolorbrewer].
+Tables were made with `modelsummary` [@citemodelsummary] package, `broom.mixed` package [@citebroom], `dplyr` package [@citedplyr], `knitr` package [@citeknitr] and `kableExtra` package [@citekableextra].
+Graphs were made with `ggplot2` package [@citeggplot].
 
@@
 # Create bar plot
-data |>
+cleaned_data |>
   ggplot(aes(x = as.factor(violation), fill = as.factor(violation))) +
@@
   )
-
 ```
@@
 
-data |> 
+cleaned_data |> 
   ggplot(aes(x = date_num)) + 
@@
   theme_minimal()
-
 ```
@@
 
-data_rise <- data %>% 
+data_rise <- cleaned_data %>% 
   filter(property_type == "High Rise" | property_type == "Low Rise")
 
-data_other <- data %>% 
+data_other <- cleaned_data %>% 
   filter(property_type != "High Rise" & property_type != "Low Rise")
@@
 
-data |> 
+cleaned_data |> 
   ggplot(aes(x = as.factor(violation), fill = as.factor(violation))) +
@@
 # Use `tidy()` for a clean tabular format
-library(broom.mixed)
 tidy_stats <- tidy(model, conf.int = TRUE)
@@
 # Round all numeric columns to 3 decimal places
-library(dplyr)
 tidy_stats <- tidy_stats %>%
@@
 # Create a table of parameter estimates
-library(knitr)
-
 tidy_stats %>%
@@
 
-# Additional data details {#sec-appx-data}
-
-# Model details {#sec-model-details}
+# Additional Data Details {#sec-appx-data}
+
+The dataset cleaning process for preparation follows several steps:
+
+1. The column names are standardized to snake_case using `janitor` package for consistency and readability.
+
+2.
+The date information in the 'inspections_closeddate' and  'inspection_opendate' columns are initially recorded in inconsistent format.
+The date information is processed and stored as a valid date type in the columns, either from the datetime (ymd_hms) or date-only (ymd) parsing using `lubridate` package.
+
+3. The dataset is then filtered to keep only cases (rows) where inspection processes were closed during 2024, i.e. 'inspections_closeddate' is on or after January 1, 2024.
+
+4.
+Time interval between the start date and end date of the inspection (i.e.
+difference in days between 'inspections_closeddate' and 'inspections_opendate') is calculated and stored as a new numeric column called 'date_num'.
+
+5.
+A new column named 'violation' is created to indicate whether there was a violation being detected in the inspection case.
+If the 'violations_item_number' presents value of 0, 'violation' is set to 0; otherwise, it is set to 1.
+
+6. Finally, only necessary column are selected and retained in the cleaned dataset: 'property_type', 'inspections_opendate', 'inspections_closeddate', 'date_num', and 'violation'.
+
+# Model Details {#sec-model-details}
 

### 2024-12-04 paper/paper.qmd
Updated final completed version of paper

@@
 
-In recent years, fire safety inspections in residential buildings have gained increasing attention from the public due to their role in ensuring the safety of residents and reducing potential dangers caused by fire-related accidents.
-Toronto Fire Services (TFS) fire prevention and enforcement strategies, which are guided by the Fire Protection and Prevention Act, 1997 (FPPA) and regulations under it (such as Ontario Fire Code), aim to increase public safety and awareness [@fire_info].
-In order to achieve this goal, TFS have been conducting inspections across a wide range of residential properties within the entire city to ensure properties' compliance with fire safety regulations.
-However, despite these efforts, there remains a limited understanding of the factors influencing the likelihood of fire safety violations across different property types and inspection durations.
-As a result, targeted interventions have not yet been effectively implemented for high-risk buildings.
-Therefore, this paper aims to analyze the impact of both inspection time interval and property type on the likelihood of violations in fire safety checks.
-By doing so, a model that provides predictions of violations based on specific features of the properties and inspection characteristics could be developed, improving TFS's ability to prioritize resources and focus on properties that require the most attention.
-
-The focus of this study is to investigate how different property types and inspection time intervals contribute to fire safety violations in Toronto, and this paper uses Bayesian logistics model to conduct predictions.
+In recent years, fire safety inspections in residential buildings have gained increasing attention from the public due to their role in ensuring the safety of residents and reducing the risks of fire-related accidents.
+Toronto Fire Services (TFS) fire prevention and enforcement strategies, which are guided by the Fire Protection and Prevention Act, 1997 (FPPA) and regulations under it (such as Ontario Fire Code), aim to enhance public safety and awareness [@fire_info].
+
+In order to achieve this goal, TFS has been conducting inspections across a wide range of residential properties throughout the city to ensure properties' compliance with fire safety regulations.
+However, despite these efforts, there remains limited understanding of the factors influencing the likelihood of fire safety violations across different property types and inspection duration.
+As a result, targeted interventions have not been effectively implemented for high-risk buildings.
+Therefore, this paper aims to analyze the impact of both inspection duration and property type on the likelihood of violations during fire safety checks.
+By doing so, the study aims to develop a model that provides predictions of violations based on specific features of the properties and inspection characteristics, thereby improving TFS's ability to prioritize resources and focus on properties that require the most attention.
+
+The focus of this study is to investigate how different property types and inspection duration contribute to fire safety violations in Toronto, using a Bayesian logistics regression model to conduct predictions.
 The predictor variables examined include the time interval of the inspection process, and the type of property being inspected.
 By exploring these factors, the paper aims to predict the likelihood of violations, conducting predictions of which property types are at higher risk for violations and how inspection duration might influence these outcomes.
-The estimand would be described in detail in @sec-estimand.
-
-As included at the end of the analysis, the model predicts with high confidence that most properties would have a high probability of being observed to have a violation of fire safety regulations.
-Such prediction by the model is confident, highlighting the utility of the model in helping to conduct targeted inspections and interventions where they are most needed.
-Moreover, the analysis further highlights that different property types have varying impacts on the likelihood of fire safety violations.
+The estimand is described in detail in @sec-estimand.
+
+As included at the end of the analysis, the model indicates that the duration of the inspection has a negligible impact on the likelihood of violations, while the variable of property type is a more significant predictor of likelihood of violations.
+The model predicts with high confidence that most properties would have a high probability of being observed to have a violation of fire safety regulations.
+This confident prediction highlights the utility of the model in identifying properties at high risk for violations, helping to conduct targeted inspections and interventions where they are most needed.
+Moreover, the analysis further suggests that different property types have varying impacts on the likelihood of fire safety violations.
 The model confidently predicts that among ten property types inspected, "High Rise," "Rooming House," and "Group Home" are more likely to have violations.
@@
 Along with "Low Rise" and "Hotel & Motel," these property types show strong evidence of being associated with higher risks of violations.
-In contrast, the model indicates that "Nursing Home" has the lowest risk of violations among ten property types inspected and some uncertainty exist in the strength of this predicted relationship.
-
-This research contributes to improving fire safety facilities in residential buildings in Toronto by providing empirical evidence and statistical predictions that supports the allocation of inspection resources based on both the property type and inspection time interval.
+In contrast, the model indicates that "Nursing Home" has the lowest risk of violations among the ten property types inspected, with some uncertainty regarding the strength of this predicted relationship.
+
+This research contributes to improving fire safety facilities in residential buildings in Toronto by providing empirical evidence and statistical predictions that supports the allocation of inspection resources based on both the property type and inspection duration.
 By highlighting which property types with how long inspection duration are most at risk for fire safety violations, the findings offer a valuable approach to prioritizing inspections and interventions.
 The results of the study have broader implications for fire safety policy, as they could be used to improve future regulatory practices and resource allocation strategies.
-By ensuring that inspection resources are concentrated on properties that present the greatest risk, this study would enhance the effectiveness of fire safety efforts, and help to reduce potential fire accidents more efficiently.
+By ensuring that inspection resources are concentrated on properties that present the greatest risk, this study would enhance the effectiveness of fire safety efforts, and help to reduce the risk of fire accidents more efficiently.
 
@@
 
-Appendix includes three parts:[Appendix -@sec-appx-survey] describes detailed idealized sampling methodology and survey designed for residents to collect fire safety feedback; [Appendix -@sec-appx-data] provides additional data details; [Appendix -@sec-model-details] presents additional details during modeling process, including posterior predictive check [Appendix -@sec-ppc], comparison between posterior and prior distributions [Appendix -@sec-pvp], and diagnostics [Appendix -@sec-diagnostics].
+Appendix includes three parts:[Appendix -@sec-appx-survey] describes detailed idealized sampling methodology and survey designed for residents to collect fire safety feedback; [Appendix -@sec-appx-data] provides additional data details in data cleaning process; [Appendix -@sec-model-details] presents additional details during modeling process, including posterior predictive check [Appendix -@sec-ppc], comparison between posterior and prior distributions [Appendix -@sec-pvp], and diagnostics [Appendix -@sec-diagnostics].
 
@@
 
-The dataset captures data related to the results of fire safety inspections conducted by Toronto Fire Services (TFS) within highrise residential buildings, which is guided by the Fire Protection and Prevention Act, 1997 (FPPA) and regulations under the FPPA, like the Ontario Fire Code [@fire_info].
-It indicates properties where violations have been found by an Inspector which are required to be fixed for compliance at the time with the Ontario Fire Code as well as properties with no observable violations [@fire_data].
+The dataset captures data related to the results of fire safety inspections conducted by Toronto Fire Services (TFS) in residential buildings in Toronto, which is guided by the Fire Protection and Prevention Act, 1997 (FPPA) and regulations under the FPPA, like the Ontario Fire Code [@fire_info].
+It includes information on properties where violations have been found by inspectors from TFS and required to correction to comply with the Ontario Fire Code at the time, as well as properties with no observable violations [@fire_data].
 
 The data collection process was conducted by TFS Fire Inspectors.
-Inspectors assess tangible aspects of fire safety based on observable and measurable attributes of the physical environment within the properties, such as proper storage of combustible materials, functionality of fire alarms and fire pumps, maintenance records for fire safety equipment and others in reference to the regulations under FPPA.
+Inspectors assess tangible aspects of fire safety based on observable and measurable attributes of the physical environment within the properties.
+This includes evaluating factors such as proper storage of combustible materials, the functionality of fire alarms and fire pumps, the maintenance records for fire safety equipment and so on, all in accordance with the regulations under FPPA.
 
 After the inspections were completed, the observations have been translated into records and written into collected data.
-The raw data entry presented by Open Data Toronto includes three main aspects: property identifier (such as address, property type), inspection information (such as inspection start and end dates), and inspection outcomes (pass or fail status for safety checks, and details of violations).
-
-Note that this dataset only includes 'closed' cases, which are cases whose inspection processes have ended.
-The ongoing inspections were not available in the dataset, and therefore would lead to potential loss of information.
-This would be further evaluated in detail in the discussion section.
+The raw data provided by Open Data Toronto includes three main aspects: property identifier (such as address, property type), inspection information (such as inspection start and end dates), and inspection outcomes (pass or fail status for safety checks, and details of violations).
+
+Note that this dataset only includes 'closed' cases, referring to those whose inspection processes have been completed.
+The ongoing inspections are not presented in the dataset, which may result in a potential loss of information.
+This limitation would be further discussed in detail in the @sec-discussion.
 
@@
 The outcome variable for the model is the violation status of the properties.
-In other words, it is the variable that represents whether the properties inspected have been found violating fire safety regulations by an Inspector or not.
-
-In the raw dataset, columns 'VIOLATION_FIRE_CODE', 'VIOLATION_DESCRIPTION' and 'VIOLATIONS_ITEM_NUMBER' indicates the outcome of the inspections.
-The previous two provides detailed information on fire code under which violation was noted.
-The latter one presents the order number of violations by code, and shows 0 if no violations observed.
-
-Therefore, a new column 'violation' is mutated to make the analysis procedure easier.
-It contains numeric values of 1 and 0, which indicates violation observed and no violation observed respectively.
-The outcome variable is thus binary.
-
-@fig-violation presents the visualized counts of properties that were found violations versus those that were not.
-The height of each bar shows the total number of cases corresponding to each category.
-We could see that the orange bar is significantly taller, indicating that among all cases selected for analysis, violations were reported more frequently in the dataset (9829 cases out of 13193).
-On the other hand, the blue bar is shorter, indicating there were fewer cases without violations (3364 cases out of 13193).
-
-In conclusion, the data contains a higher number of cases with violations (1) compared to cases where no violations were observed (0), suggesting that violations are common.
+In other words, it is the variable that represents whether the properties inspected were found to be in violation of fire safety regulations by a TFS Inspector.
+
+In the raw dataset, columns 'VIOLATION_FIRE_CODE', 'VIOLATION_DESCRIPTION' and 'VIOLATIONS_ITEM_NUMBER' indicate the outcome of the inspections.
+The first two columns provide detailed information about the fire code under which violation was noted, while the latter presents the order number of violations by code and shows 0 if no violations were observed.
+
+To simplify the analysis, a new column, 'violation', is created.
+This column contains binary values, with 1 indicating that a violation was observed and 0 indicating no violation.
+Thus, the outcome variable is binary.
 
@@
 #| label: fig-violation
-#| fig-cap: Counts of Properties that Were Found Violations versus Those that Were Not
+#| fig-cap: Counts of Properties with Violations versus Those without
 #| echo: false
@@
 
-# Create bar plot
 cleaned_data |>
@@
     x = "Violation Status",
-    y = "Count",
+    y = "Counts",
     fill = "Violation Status" # Legend title
@@
 
+@fig-violation displays the visualized counts of properties with violations versus those without.
+The height of each bar shows the total number of cases corresponding to each category.
+The orange bar is significantly taller, indicating that among all cases selected for analysis, violations were reported more frequently in the dataset (9,829 cases out of 13,193).
+In contrast, the blue bar is shorter, reflecting fewer cases without violations (3,364 cases out of 13,193).
+
+The data contains a higher number of cases with violations (1) compared to those where no violations were observed (0), suggesting that violations are relatively common.
+
 ## Predictor Variables {#sec-data-predictor}
 
-### Inspection Time Interval
-
-One predictor included in the model is the inspection time interval. It refers to the duration of the fire inspections conducted by the TFS Inspector for each case.
-
-In the raw dataset, there are two columns recording the date: 'INSPECTIONS_OPENDATE' and 'INSPECTIONS_CLOSEDDATE'.
-Previous one is the date TFS opened the inspection file, whereas the latter one is the date TFS closed inspection file or date or date enforcement proceedings ended (whichever is later).
-
-During the data cleaning process, the date is converted into time interval to enable easier analysis.
-A new column named 'date_num' is mutated by calculating the time difference between the end time and the start time of the inspection, in the unit of days.
-
-@fig-date shows the distribution of the inspection time interval.
-X-axis represents the number of days of each inspection case, and Y-axis represents the counts.
-The distribution has peak at low intervals, and the highest bar is near 0 days, indicating that a large number of properties have very short inspection time intervals.
-The right-skewed inspection suggests that as the inspection interval increases, the corresponding counts decrease stably.
-The long tail of the right-hand side of the distribution means that there are properties with very long intervals (up to 1500 days or more).
+### Inspection Duration
+
+One predictor included in the model is the inspection duration. It refers to the time interval between the start and end of the fire inspections conducted by the TFS inspectors for each case.
+
+In the raw dataset, there are two columns recording the dates: 'INSPECTIONS_OPENDATE' and 'INSPECTIONS_CLOSEDDATE'.
+The former represents the date TFS opened the inspection file, while the latter denotes the date TFS closed inspection file or the date enforcement proceedings ended (whichever is later).
+
+During the data cleaning process, these dates are converted into time interval to enable easier analysis.
+A new column, 'date_num', was created by calculating the time difference between the end and start times of the inspection, in the unit of days.
 
@@
 #| label: fig-date
-#| fig-cap: Distribution of Inspection Time Interval
+#| fig-cap: Distribution of Inspection Duration
 #| echo: false
@@
   geom_histogram(fill = "skyblue", color = "black", alpha = 0.7) +
-  labs(x = "Inspection Time Interval (Days)",
-       y = "Counts of Properties") +
+  labs(x = "Inspection Duration (Days)",
+       y = "Counts") +
   theme_minimal()
@@
 
+@fig-date illustrates the distribution of inspection duration.
+The X-axis represents the number of days for each inspection case, while the Y-axis represents the counts.
+The distribution peaks at low intervals, with the highest bar near 0 days, indicating that a large number of properties have very short inspection time intervals.
+The right-skewed shape of the distribution suggests that as the inspection duration increases, the counts of cases decrease stably.
+The long tail on the right side of the distribution means that there also exist cases with very long duration in the dataset, extending up to 1,500 days or more.
+
 ### Property Type
 
-The second predictor variable included in the model is the property type. It refers to the occupancy type of the property where the inspection took place, and is directly contains in the raw dataset.
-
-To visualize the variable, two bar plots are created separately in @fig-type.
-The left panel presents the number of occurrences of "High Rise" and "Low Rise", with the bar representing "High Rise" relatively taller, indicating a higher count compared to low rise.
-This suggests that the inspection results and data collection focus more heavily on high-rise buildings.
-
-The right panel includes the other categories of properties.
-Specifically, the types include: "Detention," "Group Home," "Group Home (VO)," "Hospital," "Hotel & Motel," "Nursing Home," "Residential Care," and "Rooming House." We could see that "Rooming House" has the highest count among these property types, whereas categories of "Detention" and "Group Home" have relatively lower counts, indicating that they are less represented in the dataset.
-
-In general, there is a diverse distribution across the property types, with some being far less frequent than others.
-High-rise properties dominate overall, while rooming houses stand out within other categories.
-The dataset might reflect an emphasis on inspecting high-rise and rooming houses more than other property types.
+The second predictor variable in the model is property type. It refers to the occupancy type of the property where the inspection took place. This variable is directly included in the raw dataset.
+
+To visualize the distribution of property types, two bar plots are created separately in @fig-type.
+The left panel presents the number of occurrences of "High Rise" and "Low Rise" properties, with the bar representing "High Rise" relatively taller, indicating a higher count compared to "Low Rise." This suggests that the inspection results and data collection focus more heavily on high-rise buildings.
+
+The right panel displays the other categories of properties, including "Detention," "Group Home," "Group Home (VO)," "Hospital," "Hotel & Motel," "Nursing Home," "Residential Care," and "Rooming House." The "Rooming House" category has the highest count among these property types, while categories of "Detention" and "Group Home" have relatively lower counts, suggesting that they are less represented in the dataset.
+
+In general, the distribution of the property types is diverse, with some types being far less frequent than others.
+High-rise properties dominate the dataset, while rooming houses are the most frequent within other categories.
+This pattern may indicate an emphasis on inspecting high-rise buildings and rooming houses than those of other property types.
 
@@
 #| label: fig-type
-#| fig-cap: Counts of Property Types
+#| fig-cap: Distribution of Property Types
 #| echo: false
@@
     x = "Property Type",
-    y = "Count",
+    y = "Counts",
     fill = "Property Type"
@@
     x = "Property Type",
-    y = "Count",
+    y = "Counts",
     fill = "Property Type" 
@@
 
-@fig-violationbytype depicts faceted bar plots showing the distribution of violation statuses (0 for no violation, 1 for violation) across different property types.
-Each subplot corresponds to a different property type.
-
-In general, property types of "Group Home," "High Rise," "Low Rise," and "Rooming House," have a higher proportion of violations (1).
-The type "Hotel & Motel" has balanced counts between 0 and 1, but violations (1) are slightly more frequent.
+@fig-violationbytype displays faceted bar plots illustrating the distribution of violation statuses (0 for no violation, 1 for violation) across different property types.
+Each subplot represents a different property type.
+
+In general, the property types of "Group Home," "High Rise," "Low Rise," and "Rooming House" show a higher proportion of violations (1).
+The type "Hotel & Motel" has relatively balanced counts between 0 and 1, but violations (1) are slightly more frequent.
 These property types may require more attention or stricter inspections.
 
-The other property types, especially "Detention" and "Nursing Home", show a much lower proportion of violations, suggesting fewer relative violation ratio.
+On the other hand, other property types, especially "Detention" and "Nursing Home," show a much lower proportion of violations, suggesting a lower relative violation rate.
 
@@
     x = "Violation Status",
-    y = "Count",
+    y = "Counts",
     fill = "Violation Status"
@@
 
-Firstly and most importantly, from the statistical standpoint, the goal is to estimate the the detection of violation from an inspection based on its time interval and the property type.
-
-Secondly, from a more practical standpoint, by predicting which type of property with how long duration is more likely to be observed violations, more efficient inspection process could be constructed.
-Identifying certain property types that would more frequently violate the fire safety regulations could provide guidelines for interventions and help to establish targeted and focused actions towards them.
-
-The model constructed in the paper is Bayesian logistics regression model designed to predict the violation status (denoted as violation) based on the fixed effect of inspection time interval (denoted as date_num) and property type (denoted as property_type).
-It is designed to predict the inspection results based on the two predictor variables.
-
-Following sections define, explain and justify each model and the variables, as well as discuss underlying assumptions, potential limitations, software used to implement the model, and evidence of model validation and checking.
+Firstly and most importantly, from a statistical perspective, the goal is to estimate the detection of violations during an inspection based on the time interval and property type.
+
+Secondly, from a more practical standpoint, by predicting which property types and inspection duration are more likely to result in violations, a more efficient inspection process could be developed.
+Identifying certain property types that have high risk to violate the fire safety regulations could provide guidelines for interventions and support implementation of targeted and focused actions.
+
+The model presented in the paper is Bayesian logistics regression model designed to predict the violation status (denoted as 'violation') based on the fixed effects of inspection duration (denoted as 'date') and property type (denoted as 'type').
+It is designed to forecast the inspection results based on these two predictor variables.
+
+The following sections define, explain and justify the model and its variables.
+They also discuss underlying assumptions, potential limitations, the software used for implementation, and provide evidence of model validation and checking.
 
@@
 
-The Bayesian model was implemented using the R programming language [@citeR], specifically utilizing the `rstanarm` package of @citerstanarm.
-This package provides an interface for fitting Bayesian regression models using Stan, and the models are fit using the package.
+The Bayesian model was implemented using the R programming language [@citeR], specifically utilizing the `rstanarm` package by @citerstanarm.
+This package provides an interface for fitting Bayesian regression models using Stan, and the models are fit using its functionality.
 
 Define $y_i$ as the binary response variable for observation $i$.
-$y_i=1$ indicates that the case has been observed violations, while $y_i=0$ indicates that no violation occurs.
-It follows a Bernoulli distribution:
+$y_i=1$ indicates that a violation has been observed, while $y_i=0$ indicates that no violation occurs.
+This follows a Bernoulli distribution:
 
@@
 
-Then define the inspection time interval for observation $i$ as date_num and the property type as property_type.
-
-The Bayesian model could be defined by the following mathematical expressions:
+Then define the inspection time interval for observation $i$ as 'date' and the property type as 'type'.
+
+The Bayesian model could be expressed with the following mathematical formulations:
 
@@
 
-- $\text{logit}(p_i) = \log\left(\frac{p_i}{1 - p_i}\right)$ is the log-odds of $p_i$.
-- $\beta_0$ is the intercept term of the Bayesian logistic regression, representing the baseline log-odds of a violation when 'date_num = 0' and 'property_type' is the reference category.
-Formula (2) specifies that $\beta_0$ follows normal distribution with mean equals 0 and variance equals $2.5^2$.
-- $\beta_1$ is the coefficient for predictor variable 'date_num‘, representing the change in log-odds of a violation per unit increase in 'date_num', the inspection time interval.
-Formula (3) specifies that $\beta_1$ follows normal distribution with mean equals 0 and variance equals $2.5^2$.
-- $\beta_2$ is the coefficient for predictor variable ’property_type', representing the change in log-odds of a violation per unit increase in 'property_type'.
-Formula (4) specifies that $\beta_2$ follows normal distribution with mean equals 0 and variance equals $2.5^2$.
+- $\text{logit}(p_i) = \log\left(\frac{p_i}{1 - p_i}\right)$ represents the log-odds of $p_i$.
+- $\beta_0$ is the intercept term of the Bayesian logistic regression, representing the baseline log-odds of a violation when $date = 0$ and 'type' is the reference category.
+Formula (2) specifies that $\beta_0$ follows normal distribution with a mean of 0 and a variance of $2.5^2$.
+- $\beta_1$ is the coefficient for predictor variable 'date', representing the change in log-odds of a violation for per unit increase in 'date', i.e., the inspection time interval.
+Formula (3) specifies that $\beta_1$ follows normal distribution with a mean of 0 and a variance of $2.5^2$.
+- $\beta_2$ is the coefficient for the predictor variable 'type', representing the change in log-odds of a violation for each unit increase in 'type'.
+Formula (4) specifies that $\beta_2$ follows normal distribution with a mean of 0 and a variance of $2.5^2$.
 
 Formula (2), (3) and (4) specifies priors for the model.
-This prior reflects the assumption that coefficients are centered around 0, with a standard deviation of 2.5, allowing moderate variability while discouraging extreme values.
-
-## Model Assumptions and Limitations {#sec-model-assume}
-
-The main, underlying assumptions and their limitations for the Bayesian model is discussed below:
+These priors reflect the assumption that the coefficients are centered around 0, with a standard deviation of 2.5, allowing for moderate variability while discouraging extreme values.
+
+## Model Assumptions {#sec-model-assume}
+
+The main assumptions for the Bayesian model and situations where the model may not be appropriate are discussed below. Limitations of the model are covered in detail in @sec-limit.
+
+- Independence of Observations
 
 Firstly, the model assumes that each observation is independent of others.
-This assumption suggests that violations at one property should not influence violations at another property unless explicitly modeled (e.g., through random effects).
-
-If observations are clustered and the assumption is violated (for instance, multiple observations were conducted in the same region or by the same inspector), overestimation and underestimation of standard errors and outcomes may occur.
-
-Secondly, the model assumes linearity in the logit. This assumption stated that the log-odds of the response variable ($\text{logit}(p_i)$) are a linear function of the predictors.
-
-If violations change non-linearly over time, the model assumption would be violated, potentially resulting in misfit of the model.
-
-Thirdly, the model assumes priors of $\text{Norma}(0,2.5)$ for the coefficients. They were constructed on domain knowledge, and poorly chosen priors could make the estimation outcome biased.
-
-Also, if new property_type levels are introduced, the model may not be no longer appropriate for the new situation, as fixed effects could not be feasible to compute estimates.
-Random effects, then, may be more appropriate.
+This assumption suggests that violations at one property should not influence violations at another property, unless explicitly modeled (e.g., through random effects).
+
+If observations are clustered (e.g., multiple observations in the same region or by the same inspector were recorded in the dataset), this assumption may be violated, leading to potential overestimation or underestimation of standard errors and outcomes.
+
+- Linearity in the Logit
+
+Secondly, the model assumes linearity in the logit. This assumption states that the log-odds of the response variable ($\text{logit}(p_i)$) are a linear function of the predictors.
+
+If violations change in a non-linear manner over time, this model assumption would be violated, potentially resulting in misfit of the model.
+
+- Prior Distributions
+
+Thirdly, the model assumes priors of $\text{Norma}(0,2.5)$ for the coefficients, based on domain knowledge. Poorly chosen priors could introduce bias into the estimation results.
+
+Also, if new levels of property type ('type') levels are introduced, the model may be no longer suitable for the new situation, as fixed effects may not be feasible for estimating the new categories.
+In such cases, random effects might be a more appropriate alternative.
 
@@
 
-Since the response variable is binary for each case and follows a Bernoulli distribution, it would be appropriate to use Bayesian logistic regression model to estimate it.
-
-The predictor variable as 'date_num' is modeled as fixed effect in the model.
-There are various reasons for this.
-Firstly, As 'date_num' represents the number of days for the inspection takes place, it is a numeric variable.
+Since the response variable is binary for each case and follows a Bernoulli distribution, a Bayesian logistic regression model is appropriate for estimating it.
+
+The predictor variable of inspection duration ('date') is modeled as a fixed effect in the model.
+There are several reasons for this choice.
+Firstly, 'date' represents the number of days on which the inspection processed, making it a numeric variable.
 Modeling it as a fixed effect allows the model to estimate its direct, continuous influence on the response variable.
-Secondly, since it applies across all observations, regardless of property type, modeling it as a fixed effect could consider its impact consistently across the entire dataset.
-It also makes the coefficient of 'date_num' ($beta_1$) be easier to interpret, avoids adding complexity to the model.
-
-The other predictor variable 'property_type' is also modeled as fixed effect.
-Since it is categorical variable, modeling it as fixed effect allow the model to estimate a separate coefficient for each category, relative to a reference level.
-This would make it easier to compare between property types, in order to understand which types of properties would be observed to have violations.
-Moreover, since 'property_type' has only 10 levels, it is feasible to compute it as fixed effect and conduct estimation without overloading the model.
-
-The prior of $\mbox{Normal}(0, 2.5)$ for every coefficients is also reasonable because it reflects prior knowledge that most predictors have small-to-moderate effects on the log-odds scale.
-This assumption would avoid overfitting to extreme values.
-
-The above final model decision is made after considering several alternative models and variants.
-One alternative is a simple linear regression model (SLR), which assumes a constant linear relationship between the predictor (violation) and the response (date_num).
-Although the model is extremely straightforward and easy to interpret, it is far too simple for estimating and neglect the key variable of 'property_type'.
-More importantly, the response variable is binary, whereas SLR assumes a continuous response variable.
-MLR also assumes so, and therefore is considered and rejected because of the same reason.
-
-Another alternative considered is the Bayesian model with natural splines (e.g.
-$f(\text{date}_i)$).
-While it could model complex, non-linear time trends and is appropriate for 'date_num', the expected model for this study does not primarily focus on exploratory analysis on non-linear relationships between date_num and violations.
+Secondly, since 'date' applies across all observations regardless of property type, modeling it as a fixed effect allows its impact to be considered consistently across the entire dataset.
+This also makes the coefficient of 'date' ($beta_1$) be easier to interpret and avoids adding unnecessary complexity to the model.
+
+The other predictor variable, property type ('type'), is also modeled as a fixed effect.
+Since it is categorical variable, modeling it as a fixed effect enables the model to estimate a separate coefficient for each category, relative to the reference level.
+This makes it easier to compare different property types, in order to understand which types of properties are more likely to have violations.
+Moreover, since 'property_type' has only 10 levels, it is feasible to compute it as a fixed effect and develop estimation without overloading the model.
+
+The prior of $\mbox{Normal}(0, 2.5)$ for each coefficient is reasonable because it reflects prior knowledge that most predictors have small-to-moderate effects on the log-odds scale.
+This assumption helps prevent overfitting by discouraging extreme values.
+
+The final model choice was made after considering several alternative models.
+One alternative is a simple linear regression (SLR) model, which assumes a constant linear relationship between the predictor (violation) and the response (date).
+While straightforward and easy to interpret, this model is too simplistic for estimation, neglecting the important variable of property type (type).
+More importantly, the response variable is binary, and SLR assumes a continuous response, making it unsuitable for this case.
+Multiple linear regression (MLR) also assumes a continuous response variable, so it was similarly rejected.
+
+Another alternative considered was a Bayesian model with natural splines (e.g.
+$f(\text{date}_i)$), which could model complex, non-linear time trends and would be appropriate for 'date'.
+However, the expected model for this study does not primarily focus on exploratory analysis on non-linear relationships between 'date' and 'violation'.
 Non-linear functions would also overfit the data if not regularized properly.
 
-While considering alternative Bayesian logistics model, the model with 'property_type' as fixed effect was also considered.
-This would capture variability across property types without explicitly estimating coefficients for each type, and does not provide explicit estimates for each property type.
-The model would be suitable if there are many property types, but the number of types is manageable to include it in the model as fixed effect.
-
-Therefore, after considering many alternatives, the final model of Bayesian logistics model with 'date_num' and 'property_type' as fixed effect is chosen.
-It could directly provides explicit comparisons between property types without overfitting the model, and meet the focus of the research question.
+Additionally, a Bayesian logistic model with property type ('type') as a random effect was considered.
+This would capture variability across property types without explicitly estimating coefficients for each type.
+While this model would be suitable if there were many property types, it was unnecessary given the manageable number of property types in this case.
+
+Therefore, after considering these alternatives, the final model of Bayesian logistics model with inspection duration ('date') and property type ('type') as fixed effects was chosen.
+This model allows for direct, explicit comparisons between property types without overfitting the model, and aligns with the focus of the research question.
 
@@
 
-Our results of the Bayesian logistic regression model are summarized in @tbl-modelresults. The table provides information of coefficients and main summary statistics.
+The results of the Bayesian logistic regression model are summarized in @tbl-modelresults. The table provides information about the coefficients and main summary statistics.
 
 The table firstly lists estimates of coefficients for all parameters.
-The first line suggests an intercept of -6.72 for the model, indicating very low baseline odds of a violation for the reference property type when date_num = 0.
-The second line presents that the estimated coefficient for date_num is 0.02, which is very small and suggests that the inspection time interval has negligible effect on the violation outcome of observations.
-
-Then the table shows the coefficients for every property type respectively.
-All property types show large positive coefficients, meaning that they increase the log-odds of violations and have higher risk of violation compared to the reference property type.
-For instance, for property type of "Group Home", it increases log-odds of violation by 5.88; for property type of "High Rise", it increases log-odds of violation by 6.21; for property type of "Hospital", it increases log-odds of violation by 4.67; etc.
-It could be observed that "Nursing Home" has the smallest coefficient, and thus has the smallest effect on violation.
-However, it still contribute positively to the log-odds.
+The first line suggests an intercept of -6.72 for the model, indicating very low baseline odds of a violation for the reference property type when $date = 0$.
+The second line shows that the estimated coefficient for predictor 'date' is 0.02, which is very small and suggests that the inspection duration has a negligible effect on the violation outcome of observations.
+
+The table then presents the coefficients for every property type respectively.
+All property types show large positive coefficients, meaning that they increase the log-odds of violations and have a higher risk of violation compared to the reference property type.
+For example, for the property type of "Group Home", the log-odds of violation increases by 5.88; for the property type of "High Rise", the increase is 6.21; for the property type of "Hospital", the increase is 4.67; and so on.
+It could be observed that "Nursing Home" has the smallest coefficient, suggesting that it has the smallest effect on the likelihood of violations.
+However, it still contributes positively to the log-odds of a violation.
 
 The table also presents summary statistics of the model.
-One of the important results include $R^2=0.342$.
-$R^2$ is the proportion of the variation in the dependent variable that is predictable from the independent variables [@wiki_rsquare].
-R-squared of 0.342 suggests that 34.2% of the variability in the response variable (violation) is explained by the model, which is relatively good for logistic regression.
-Moreover, the RMSE (Root Mean Squared Error) value of 0.32 shows the average deviation between predicted probabilities and observed outcomes.
-This value is low, indicates a satisfactory fit for the model.
+One of the important results is $R^2=0.342$.
+$R^2$ refers to the proportion of the variation in the dependent variable that is predictable from the independent variables [@wiki_rsquare].
+An R-squared value of 0.342 suggests that 34.2% of the variability in the response variable ('violation') is explained by the model, which is relatively good for logistic regression.
+Moreover, the RMSE (Root Mean Squared Error) value of 0.32 indicates the average deviation between predicted probabilities and observed outcomes.
+This value is low, suggests a satisfactory fit for the model.
 
@@
 #| label: tbl-modelresults
-#| tbl-cap: "Explanatory Models of Probability of Violation based on Inspection Time Interval and Property Type"
+#| tbl-cap: "Explanatory Model of Probability of Violation based on Inspection Duration and Property Type"
 #| warning: false
@@
 @tbl-posteriorestimate shows more detailed information about the coefficients of each parameter.
-Column "Estimate" presents the mean posterior estimate for the effect of each parameter on the log-odds of the outcome (violation); "Std.Error" presents the standard deviationor the uncertainty in the estimate; "Conf.Low" and "Conf.High" are the lower and upper bounds of the 95% credible interval for the parameter, showing the range of plausible values.
+The "Estimate" column presents the mean posterior estimate for the effect of each parameter on the log-odds of the outcome ('violation'); The "Std.Error" column presents the standard deviation, or the uncertainty, in the estimate; The "Conf.Low" column and the "Conf.High" column present the lower and upper bounds of the 95% credible interval for the parameter, illustrating the range of plausible values for the effect of the parameter.
 
@@
 
-Main interpretation for this code focuses on 95% confidence interval.
-In general, if the credible interval does not include 0, the effect of the variable is statistically significant, indicating that the model is confident about the relationship.
-Most of the parameters have credible intervals excluding value 0, and some intervals are far from 0, suggesting that there's strong evidence supporting their effect on the violation outcome.
-For instance, the property type of "High Rise" has 95% CI of $[3.25, 10.45]$, showing that the model is confident about the significant effect of the increased contribution by high rise buildings to log-odds of violations.
-
-On the other hand, two parameters have 95% confidence interval including 0, which are property types of "Group Home (VO)" and "Nursing Home".
-This represents that the effect of the variables on violations is not statistically significant, and the relationship is uncertain.
-Further data collection may be needed to better understand their relationship with violations.
-
-@fig-95ci visualizes the parameter estimate values and their credible intervals for easier presentation.
+The main interpretation for the code focuses on the 95% confidence interval.
+In general, if the credible interval does not include 0, the effect of the variable is considered statistically significant, indicating that the model is confident in the relationship.
+Most of the parameters have credible intervals that exclude 0, with some intervals being far from 0, suggesting that there is strong evidence supporting their effect on the violation outcome.
+For example, the property type of "High Rise" has a 95% CI of $[3.25, 10.45]$, showing that the model is confident in the significant effect of high-rise buildings on the log-odds of violations, with a substantial contribution to the likelihood of violations.
+
+On the other hand, two parameters have 95% CI that includes 0, which are property types of "Group Home (VO)" and "Nursing Home".
+This represents that the effect of these variables on violations is not statistically significant, and the relationship remains uncertain.
+Further data collection may be necessary to better understand their relationships with violations.
+
+@fig-95ci visualizes the parameter estimate values and their credible intervals for clearer presentation.
 
@@
 @fig-predictprob plots the distribution of predicted probabilities for the model.
-X-axis represents the predicted probabilities ($p_i$) of the outcome for each observation in the dataset, and the values of probabilities are bounded from 0 to 1.
-Y-axis represents the relative density of observations iwth particular predicted probabilities.The density curve on the graph represents the estimated density of predicted probabilities, and the curve's height reflects how concentrated the predicted probabilities are around specific values.
+The X-axis represents the predicted probabilities ($p_i$) of the outcome for each observation in the dataset, with values ranging from 0 to 1.
+The Y-axis represents the relative density of observations with particular predicted probabilities.
+The density curve on the graph represents the estimated density of predicted probabilities, and the curve's height reflects how concentrated the predicted probabilities are around specific values.
 
@@
 
-The plot shows that the distribution has higher peak, which also means higher density, around $p=1$.
+The plot shows that the distribution has higher peak, which means a higher density, around $p=1$.
 On the other hand, the peak around $p = 0$ is slightly lower.
-This indicates more confident predictions for observations with a high probability of a violation, meaning that the model predicts a larger proportion of observations with high confidence that a violation is likely to occur.
+This indicates more confident predictions for observations with a high probability of violations, meaning that the model predicts a larger proportion of observations with high confidence that a violation is likely to occur.
 
@@
 
-The results of the Bayesian logistic regression model indicates that the duration of the inspection has a negligible impact on the likelihood of violations, whereas the predictor variable of property type plays a more significant role in determining violations.
+The results of the Bayesian logistic regression model indicate that the duration of the inspection has a negligible impact on the likelihood of violations, while the variable of property type is a more significant predictor of likelihood of violations.
 The model predicts with high confidence that most properties would have a high probability of being observed to have a violation of fire safety regulations, shown by the distribution of predicted probabilities.
-Such prediction by the model in identifying properties at high risk of violations is confident, highlighting the utility of the model in helping to conduct targeting inspections and interventions where they are most needed.
+This confident prediction highlights the utility of the model in identifying properties at high risk for violations, helping to conduct targeted inspections and interventions where they are most needed.
 
 The analysis further highlights that property types have varying impacts on the likelihood of fire safety violations.
-Among the property types, "High Rise", "Rooming House" and "Group Home" have the highest risk of violations compared to the reference property type, shown by the large, positive coefficients.
+Among the property types, "High Rise," "Rooming House," and "Group Home" have the highest risk of violations compared to the reference property type, as evidenced by the large, positive coefficients.
 These property types are followed by "Low Rise" and "Hotel & Motel," which also show relatively high risks of violations.
-For these five property types, there is strong evidence supporting their relationship with the likelihood of violations, as their 95% confidence intervals do not include zero, suggesting a statistically significant impact.
-
-On the other hand, "Nursing Home" shows the smallest coefficient with confidence interval including zero, suggesting a relatively lowest risk of violations and some uncertainty regarding the strength of the relationship.
+For these five property types, there is strong evidence supporting their relationship with the likelihood of violations, as their 95% credible intervals do not include zero, suggesting a statistically significant impact.
+
+On the other hand, "Nursing Home" shows the smallest coefficient, with CI including zero.
+This suggests a relatively lowest risk of violations and some uncertainty regarding the strength of the relationship.
 Despite this, "Nursing Home" still demonstrates a positive, though weaker, risk of violations compared to other property types.
@@
 
-The analysis includes two main predictor variables: the inspection time interval and property type.
-The inspection time interval refers to the duration between the start and end date of the inspection, and property type includes ten categories, such as high-rise buildings, low-rise buildings, group homes, and others.
+The analysis includes two main predictor variables: the inspection duration and property type.
+The inspection duration refers to the time interval between the start and end date of the inspection, and property type includes ten categories, such as high-rise buildings, low-rise buildings, group homes, and others.
 These two variables were selected based on their potential to influence the outcome of fire safety inspections.
@@
 
-The study employs a Bayesian logistic regression model to analyze the data, allowing for the prediction of the likelihood of violations and considering uncertainty around the estimates at the same time.
-The results of the model are stated as follows: the model predicts with high confidence that most properties would have a high probability of being observed to have a violation of fire safety regulations; Different property types have varying impacts on the likelihood of fire safety violations; Duration of the inspection has a negligible impact on the likelihood of violations; Among ten property types inspected, "High Rise," "Rooming House," and "Group Home" are more likely to have violations and therefore should receive more targeted inspections and interventions.
+The study employs a Bayesian logistic regression model to analyze the data, allowing for the prediction of the likelihood of violations while considering uncertainty around the estimates at the same time.
+The results of the model are stated as follows: the model predicts with high confidence that most properties would have a high probability of being observed to have a violation of fire safety regulations; Different property types have varying impacts on the likelihood of fire safety violations; Duration of the inspection has a negligible impact on the likelihood of violations; Among ten property types inspected, "High Rise," "Rooming House," and "Group Home" are more likely to have violations, suggesting that these property types should receive more targeted inspections and interventions.
 
 Overall, the paper identifies the role of property type as a key factor influencing fire safety regulation violation status in Toronto.
-The findings of the study could then be used to motivate targeted inspections and interventions, allowing fire prevention resources to be concentrated on properties that present the highest risk.
-Prioritizing high-risk buildings enhances the effectiveness of fire safety efforts, and helps to reduce potential fire accidents more efficiently.
+The findings of the study could then be used to motivate targeted inspections and interventions, enabling fire prevention resources to be concentrated on properties that present the highest risk.
+Prioritizing high-risk buildings enhances the effectiveness of fire safety efforts, and helps to reduce the likelihood of fire accidents more efficiently.
 
@@
 Toronto Fire Services may reconsider the emphasis placed on inspection duration.
-If longer inspections are not significantly improving the detection of violations, resources could be better spent on other aspects of the inspection process, such as using advanced fire safety technologies, improving inspector training, or focusing on properties with higher violation risks.
+If longer inspections are not significantly improving the detection of violations, resources could be better spent on other aspects of the inspection process, such as using high-quality fire safety technologies, improving inspector training, or focusing on properties with higher violation risks.
 This could make the inspection process be more cost-effective by reducing the time spent on inspections, while still maintaining the quality of fire safety prevention procedure.
@@
 
-## Weaknesses and Limitations
+## Weaknesses and Limitations {#sec-limit}
 
@@
 
-Fire safety inspections in residential buildings provide a critical mechanism for ensuring compliance with fire safety regulations.
-However, the dataset presenting inspection outcomes and analysis based on it only reflects the violation status before the enforcement procedure ends.
+Fire safety inspections in residential buildings provide a mechanism for ensuring compliance with fire safety regulations.
+However, the dataset, which presents inspection outcomes and analysis, only reflects the violation status before the enforcement procedure ends.
 It fails to provide information about whether buildings will maintain compliance or revert to unsafe practices after the inspection process ends.
-Since frequent routine inspections are often expensive and therefore impossible, it is necessary to explore alternative methods for monitoring the fire safety status of the properties and evaluating the long-term effectiveness of previous inspections.
-
-Introducing a resident survey fills these gaps by collecting the experiences and insights of those who are most directly affected by fire safety measures.
-Residents live in these buildings are familiar with the day-to-day reality of fire safety status, and could provide honest feedback and valuable perspective on whether inspections have resulted in improvements, or whether the properties conduct actions that violate regulations again.
-
-This approach not only offers real-time updates of the violation status of the properties, but is also cost-effective.
-By incorporating resident surveys, the monitoring process becomes more sustainable, enhancing the overall understanding of fire safety compliance beyond the inspection period.
+Since frequent routine inspections are often expensive and therefore impractical, it is necessary to explore alternative methods for monitoring the fire safety status of properties and evaluating the long-term effectiveness of previous inspections.
+
+Introducing a resident survey addresses such concerns by collecting the experiences and thoughts of those who are most directly affected by fire safety measures.
+Residents, who live in these buildings, are familiar with the day-to-day status of fire safety, and could provide honest feedback and valuable perspectives on whether inspections have led to improvements, or whether the properties have resumed practices that violate regulations.
+
+This approach not only offers real-time updates of the violation status of properties, but is also cost-effective.
+By incorporating resident surveys, the monitoring process becomes more sustainable, enhancing the overall understanding of fire safety compliance that extends beyond the inspection period.
 
@@
 
-- Assess Perceived Changes After Inspections: Determine if residents have noticed any improvements or changes in fire safety measures after the inspection and enforcement procedure ends, offering valuable feedback on the effectiveness of the interventions made.
-
-- Identify Recurring Issues in Residential Buildings: Collect residents' observations and feedback on recurring violations of fire safety regulations in the properties, helping to highlight areas that may need further attention or action.
-
-- Improve Policies Related to Fire Safety: Provide down-to-earth perspective from residents to improve regulatory practices related to fire safety, ensuring that policies are better aligned with the needs and experiences of those directly affected.
-This can also guide more effective resource allocation to address ongoing safety concerns.
-
-- Arise Residents' Awareness of Fire Safety: Determine whether residents are aware that a fire safety inspection has taken place in their buildings, and to what extent residents recognizes the importance of fire safety.
-The survey, therefore, aimed to emphasize to residents that fire safety inspections are not just a property-level concern, but an issue that affects everyone living in the building.
-By highlighting the collective responsibility for fire safety, the survey sought to encourage residents to take an active role in the ongoing maintenance and improvement of fire prevention measures, and to promote voluntary compliance with fire safety regulations, ensuring that all residents contribute to maintaining a safe living environment for everyone in the building.
+- Assess Perceived Changes After Inspections: Determine whether residents have noticed any improvements or changes in fire safety measures after the inspection and enforcement procedures, providing valuable feedback on the effectiveness of the inspections conducted.
+
+- Identify Recurring Issues in Residential Buildings: Collect residents' observations and feedback on recurring violations of fire safety regulations in the properties, helping to highlight areas that may require further attention or action.
+
+- Improve Policies Related to Fire Safety: Offer down-to-earth perspective from residents to improve regulatory practices related to fire safety, ensuring that policies aligned more closely with the needs and experiences of those directly affected.
+Such approach also guide more effective resource allocation to address ongoing safety concerns.
+
+- Raise Residents' Awareness of Fire Safety: Determine whether residents are aware of fire safety inspections conducted in their buildings, and the extent to which they recognize the importance of fire safety.
+The survey, therefore, aims to emphasize that fire safety inspections are not only a property-level concern, but an issue that affects everyone living in the building.
+By highlighting the collective responsibility for fire safety, the survey sought to encourage residents to actively participate in the ongoing maintenance and improvement of fire prevention measures.
+It also aims to promote voluntary compliance with fire safety regulations, ensuring that all residents contribute to maintaining a safe living environment for everyone in the building.
 
@@
 
-Target population refers to the population of the survey's interest.
-The target population for this fire safety feedback survey includes all residents of residential buildings in Toronto that have undergone fire safety inspections within the last 12 months, varying in property type and geographic location within the city.
+Target population refers to the group of individuals of the survey's interest.
+For this fire safety feedback survey, the target population includes all residents of residential buildings in Toronto that have undergone fire safety inspections within the last 12 months, varying in property type and geographic location within the city.
 
@@
 The sampling frame or pool of potential respondents represents all the people in the population potentially to be sampled and invited to the survey [@howtorunsurveys].
-In this research, the sampling frame will be based on a list of properties from inspection records.
-The survey will be distributed by contacting the building management or tenant associations of those properties, who will then send the surveys to the residents for completion.
+In this research, the sampling frame will be based on a list of properties derived from inspection records.
+The survey will be distributed by contacting the building management or tenant associations of these properties, who will then send the surveys to the residents for completion.
 
@@
 
-To ensure the survey on fire safety compliance gathers reliable and representative data, a stratified random sampling method will be employed.
-The sampling approach follows the guidelines in "Survey Methodology" [@surveymethodology].
-
-This approach divides the frame of population elements into meaningful subgroups, or "strata", which are "mutually exclusive groups of elements on a sampling frame" [@surveymethodology].
-Then, separate samples are drawn from each stratum, using randomization techniques (e.g.
-random number generators) to select participants within each stratum.
+To ensure that the survey on fire safety compliance gathers reliable and representative data, a stratified random sampling method will be employed.
+The sampling approach follows the guidelines outlined in Survey Methodology [@surveymethodology].
+
+This approach involves dividing the frame of population elements into meaningful subgroups, or "strata", which are "mutually exclusive groups of elements on a sampling frame" [@surveymethodology].
+Then, separate samples are drawn from each stratum, using randomization techniques (e.g., random number generators) to select participants within each stratum.
+This approach helps ensure that the sample accurately reflects the diversity of the population.
 
@@
 
-- Region: The geographic address of the property, ensuring representation from different areas within Toronto.
+- Region: The geographic address of the property, ensuring that different areas within Toronto are represented.
 
@@
 
-This study plans to mount a survey collecting feedback of fire safety inspection of properties and expect that the results vary across different property types and regions in Toronto.
-Therefore, the strata will be defined based on key characteristics relevant to building types and location information.
+This study plans to mount a survey collecting feedback on fire safety inspections of properties and expect that the results will vary across different property types and regions in Toronto.
+Therefore, the strata will be defined based on key characteristics relevant to building types and location information, ensuring that diverse perspectives are represented in the survey results.
 
@@
 
-The planned or target sample is all the people that ideally to be included to complete the survey [@howtorunsurveys].
-
-The sample size should be determined by both considering to achieve statistical significance and to meet resource constraints.
-After obtaining information about sample frame size, or the total number of residents across all strata, the proportion of the planned sample size allocated to each stratum should match the proportion of that stratum in the overall target population.
+The planned or target sample refers to all the people that ideally to be included to complete the survey [@howtorunsurveys].
+
+The sample size should be determined by balancing the need to achieve statistical significance with the constraints of available resources.
+After obtaining information about sample frame size, or the total number of residents across all strata, the proportion of the planned sample size allocated to each stratum should align with the proportion of that stratum in the overall target population.
 
@@
 
-Coverage error is the difference between the potential pool of respondents and the target population [@howtorunsurveys].
-In other words, the sampling frame does not fully represent the target population.
+Coverage error refers to the difference between the potential pool of respondents and the target population [@howtorunsurveys], meaning that the sampling frame does not fully represent the target population.
 
 In this research, the surveys will be distributed to residents using online Google Forms.
-However, since the recruitment relies on digital methods, there is a potential risk of underrepresentation for properties in regions or with property types where a majority of residents lack internet access or digital literacy.
+However, since the recruitment relies on digital methods, there is a potential risk of underrepresentation in regions or property types where a majority of residents lack internet access or digital literacy.
 This could result in skewed data, with certain populations being less likely to participate.
@@
 Additionally, since the sampling frame is based solely on official building management contact information, residents in informal or unregistered housing arrangements may be excluded from the survey.
-This limitation could further affect the representativeness of the sample, as it excludes individuals living in non-official housing setups who may also be affected by fire safety measures.
+This limitation could further affect the representativeness of the sample, as it excludes individuals living in non-official housing setups, who may also be affected by fire safety measures.
 
@@
 
-In this research, despite randomization, it may still be possible that the selected individuals within a stratum do not represent the overall stratum accurately.
-This could occur due to certain individuals being overrepresented or underrepresented by chance.
+In this research, despite the use of randomization, it is still possible that the selected individuals within a stratum do not accurately represent the overall stratum.
+This could occur due to the chance overrepresentation or underrepresentation of certain individuals.
 As a result, while randomization aims to minimize bias, sampling error could still influence the accuracy and precision of the findings.
@@
 
-In this research, the error could arise due to the residents not receiving or seeing the invitation of the survey.
-Since the surveys are distributed by building management or tenant associations through online platforms such as emails, there is a risk that the survey invitations may be overlooked or filtered into spam folders.
-Email-based distribution depends on residents regularly checking their inboxes, and not every resident has such habit.
-If the email is sent from an unfamiliar address or lacks clear identification, residents might dismiss it as junk or advertising mail, and ignore it entirely.
+In this research, error could arise if residents do not receive or notice the invitation of the survey.
+Since the surveys are distributed by building management or tenant associations through online platforms such as email, there is a risk that the survey invitations may be overlooked or filtered into spam folders.
+Email-based distribution depends on residents regularly checking their inboxes, and not all residents will do so.
+If the email is sent from an unfamiliar address or lacks clear identification, residents might dismiss it as junk or advertising mail, potentially ignoring it entirely.
 Furthermore, some email systems automatically filter certain messages into spam folders, reducing the visibility of the survey and limiting participation.
 
-Additionally, residents may ignore the survey invitation, potentially due to the lack of immediate rewards or incentives for participation.
+Additionally, residents may ignore the survey invitation due to a lack of immediate rewards or incentives for participation.
 Without clear incentives, such as gift cards or other tangible rewards, residents may not feel motivated to take the time to complete the survey.
@@
 
-- The survey is estimated to take about 10 minutes to complete.
+- The survey is estimated to take about 5 minutes to complete.
 
@@
 
-The designing process of the survey has drawn from the guidance in the paper “How to Run Surveys” [@howtorunsurveys].
-The following considerations address the potential biases in the proposed resident survey on fire safety compliance and suggest practical solutions:
+The designing process of the survey is informed by the guidance provided in the paper “How to Run Surveys” [@howtorunsurveys].
+The following considerations address the potential biases in the proposed resident feedback survey on fire safety compliance and suggest practical solutions:
 
@@
 
-This type of bias occurs as respondents "try to take short cuts to minimize the cognitive load" [@howtorunsurveys].
-They may also be natural consequences of how people process information based on the serial position of alternatives and their visual presentation.
-Typical bias includes: moderacy biases, extreme response biases, and response Order biases.
+Response bias occurs when respondents "try to take short cuts to minimize the cognitive load" [@howtorunsurveys], which could lead to skewed results.
+This bias could also arise from how people process information based on the serial position of alternatives and their visual presentation.
+Common types of response bias include: moderacy biases, extreme response biases, and response order biases.
 In other words, respondents may consistently select moderate or extreme options, or may be influenced by the order in which options are presented.
@@
 Stefanie Stantcheva suggests that randomizing the order of response options for questions with unordered (nominal) response options would be one of the solutions to the response biases.
-According to this recommendation, the fire safety feedback survey has been designed to randomly arrange the order of options for questions related to functionality and accessibility of fire safety facilities in the buildings in section 4.
-These questions followed a consistent and same structure and logic, making them particularly vulnerable to response biases due to the potential influence of the order in which options are presented.
-Randomizing the response options mitigates effects for such biases, enhancing the reliability of the data collected.
+Following this recommendation, the fire safety feedback survey has been designed to randomly arrange the order of options for questions related to functionality and accessibility of fire safety facilities in the buildings, as outlined in Section 4 in the survey.
+These questions follow a consistent structure and logic, making them particularly vulnerable to response biases due to the potential influence of the order in which options are presented.
+Randomizing the response options mitigates the effects of such biases, thereby enhancing the reliability of the data collected.
 
 Stefanie Stantcheva also recommends avoiding long response lists, as they can overwhelm respondents and introduce bias.
-Therefore, most of the survey questions do not require respondents to read through extensive lists of alternatives and choices, unless necessary.
-This approach aims to enhance the clarity and make respondents feel less stressful in completing the survey.
-
-Balanced scales, such as a 5-point Likert scale with clear and evenly distributed options, could also help reduce the negative effects of the response bias by providing a range of numeric, direct choices to the respondents.
-In accordance with this principle, the survey includes several scaled questions, such as "On a scale of 1 to 5, how effective do you think the changes have been in improving fire safety in your building?"
+Therefore, most of the questions in the fire safety feedback survey are designed to avoid requiring respondents to read through extensive lists of alternatives and choices, unless necessary.
+This approach aims to enhance the clarity and reduce the stress respondents may feel when completing the survey.
+
+Additionally, balanced scales, such as a 5-point Likert scale with clear and evenly distributed options, could help reduce the negative effects of response bias by providing a range of numeric, direct choices to the respondents.
+Following this principle, the survey includes several scaled questions, such as "On a scale of 1 to 5, how effective do you think the changes have been in improving fire safety in your building?"
 
@@
 
-Stefanie Stantcheva suggests that by assuring respondents of complete anonymity in the survey, the social desirability biases could be mitigated, since emphasizing the confidentiality of responses would reduce pressure for the respondents to conform.
-
-According to this advice, the fire safety feedback survey has included special emphasis on anonymity at the beginning in the introduction section, clearly informing respondents that their answers "will all be treated with complete confidentiality and anonymity." This assurance is intended to encourage honest and open responses, helping to aviod situations where respondents provide socially desirable answers rather than their true opinions.
+Stefanie Stantcheva suggests that by assuring respondents of complete anonymity in the survey, the social desirability biases could be mitigated, since emphasizing the confidentiality of responses would reduce pressure for the respondents and encourage more honest feedback.
+
+Following this advice, the fire safety feedback survey includes special emphasis on anonymity in the introduction section, clearly informing respondents that their answers "will all be treated with complete confidentiality and anonymity." This assurance is intended to encourage honest and open responses, reducing the likelihood of respondents providing socially desirable answers instead of their true opinions.
 
 This fire safety feedback survey also uses neutral wording and avoids leading questions.
-For instance, instead of asking, “Do you think the building is safer now?”, the survey asks, “Have you noticed any changes in safety measures?” This approach ensures that respondents are not influenced by biased or suggestive language, allowing them to provide more objective and accurate feedback based on their own observations and thoughts.
+For instance, instead of asking, “Is the fire alarm working well?”, the survey asks, “How is the fire alarm functionality in your building?” This approach ensures that respondents are not influenced by biased or suggestive language, allowing them to provide more objective and accurate feedback based on their own observations and thoughts.
 
@@
 
-As recommended by Stefanie Stantcheva, the fire safety feedback survey is designed to provide a smooth respondent experience, ensuring that the survey is visually clear and user-friendly to reduce dropout rates.
-The survey only includes only necessary, non-complex questions to keep it concise and short, ensuring that respondents do not feel overwhelmed or impatient while completing it.
+As recommended by Stefanie Stantcheva, the fire safety feedback survey is designed to provide a smooth respondent experience, ensuring that the survey is visually clear and user-friendly, which helps reduce dropout rates.
+The survey includes only necessary, non-complex questions to keep it concise and short, preventing respondents from feeling overwhelmed or impatient while completing it.
 By focusing on essential topics, the survey aims to encourage accurate responses without causing respondents to drop out.
@@
 Stefanie Stantcheva also suggests the survey provide strong incentives for the respondents, in order to encourage respondents to complete the survey thoroughly and maximize participation.
-This could include offering a variety of possible rewards that appeal to a broad range of people, preventing not only attrition but also selection biases.
-
-If budget allows, offering cash or gifts as rewards could motivate the audience to participate, ensuring that the response rate remains high throughout the survey process.
+This could involve offering a variety of possible rewards that appeal to a broad range of people, helping to prevent both attrition and selection biases.
+
+If the budget allows, offering cash or gifts as rewards could further motivate the audience to participate, ensuring that the response rate remains high throughout the survey process.
 
@@
 
-During the modeling process, posterior predictive checks (PPC) is used.
-
-PPC is the comparison between what the fitted model predicts and the actual observed data, which validates whether the fitted model is compatible with the observed data.
+During the modeling process, posterior predictive checks (PPC) are used.
+
+PPC involves the comparison between what the fitted model predicts and the actual observed data, which validates whether the fitted model is compatible with the observed data.
 The aim is to detect if the model is inadequate to describe the data [@ppcheck].
@@
 
-In this PPC plot, x-axis represents predicted probability of the binary outcome $p_i$, which is the probability of observing violation for a property during inspection; y-axis represents density or frequency of the predicted probabilities or aggregated counts.
-
-The dark black line presents the distribution of the observed outcome ($y$), which is a smoothed estimate of the distribution of binary response 'violation'.
-On the other hand, the light blue lines represent the posterior predictive simulations, which are the density of the replicated data ($y_{rep}$) generated from the posterior predictive distribution of the fitted model.
+In this PPC plot, the X-axis represents predicted probability of the binary outcome $p_i$, which is the probability of observing violation for a property during the inspection.
+The Y-axis represents density or frequency of the predicted probabilities or aggregated counts.
+
+The dark black line represents the distribution of the observed outcome ($y$), which is a smoothed estimate of the distribution of the binary response 'violation'.
+On the other hand, the light blue lines represent the posterior predictive simulations, which are the densities of the replicated data ($y_{rep}$) generated from the posterior predictive distribution of the fitted model.
 
 Whether the black line matches well with the blue lines indicates how well the model fits the observed data.
-If the black line aligns well with the blue lines, it suggests that the model is performing well in capturing the actual data distribution, and vice versa.
+If the black line aligns closely with the blue lines, it suggests that the model is performing well in capturing the actual data distribution.
+Conversely, a significant mismatch would suggest that the model may not adequately describe the data.
 
@@
 
-The plot shows that the curves for $y$ (observed data) and $y_rep$ (posterior predictive distribution) align closely with each other, suggesting that the fix effects of two predictor variables capture the overall pattern of the observed data well, and the Bayesian model generates predictions consistent with the observed data.
-Lack of mismatches between curves mean that the model provides good fit of data.
-Near extreme probabilities of 0 and 1, two curves tightly follow each other, indicating that the model correctly predicts extreme outcomes.
+The plot shows that the curves for $y$ (observed data) and $y_rep$ (posterior predictive distribution) align closely with each other, suggesting that the fix effects of two predictor variables capture the overall pattern of the observed data well, and the Bayesian model generates predictions that are consistent with the observed data.
+The lack of significant mismatches between the curves means that the model provides a good fit of data.
+Near extreme probabilities of 0 and 1, the two curves tightly follow each other, indicating that the model correctly predicts extreme outcomes.
 
@@
 
-Comparing the posterior distribution with the prior one is also necessary for model validation. It examines how the model fits and is affected by the data.
-
-Prior distribution represents the beliefs about the parameter values before observing any data, which is constructed by our initial assumptions.
+Comparing the posterior distribution with the prior distribution is necessary for model validation. It examines how the model fits and is affected by the data.
+
+The prior distribution represents beliefs about the parameter values before any data is observed, based on the initial assumptions.
 In the plot, it is represented by horizontal lines with points centered at the prior mean (in this case, 0) in the right panel.
 
-Posterior distribution reflects updated beliefs about the parameters after observing the data.
-It is represented by points (means or medians), which have colors representing the parameters respectively, and horizontal lines, which are credible intervals, derived from the data.
-The shorter horizontal lines, the narrower credible intervals, the more the reduced uncertainty for the parameter estimation after incorporating the data.
+The posterior distribution reflects updated beliefs about the parameters after observing the data.
+It is represented by points (means or medians), with colors representing the parameters respectively, and horizontal lines representing credible intervals derived from the data.
+The shorter the horizontal lines, the narrower the credible intervals, indicating that the uncertainty in the parameter estimation is reduced after incorporating the data.
 
@@
 
-@fig-posteriorvsprior compares the posterior with the prior distribution of the Bayesian model included in this paper, validating whether the data has a significant impact on the parameter estimates and whether the model is well-fit.
-
-In general, each level shows a narrower posterior distribution than the prior, reflecting that the uncertainty decreases and the data provides substantial information to update the prior beliefs.
-Parameters with credible intervals far from zero in the posterior are strongly influenced by the data and have meaningful effects, such as property type of 'Rooming House' (prprty_typRH) and 'Group Home' (prprty_typeGH).
-
-Shown by the point representing 'Intercept', the posterior credible interval is narrower than the prior, suggesting strong data support for it.
-The negative posterior mean indicates that the baseline log-odds of a violation for the reference property type (when date_num = 0) is below 0 (i.e., a low probability of violation).
-
-The posterior point for date_num is very narrow and centered near 0, suggesting that the data indicates little or no effect of inspection time interval on the log-odds of a violation.
-The credible interval includes 0, reinforcing the lack of a strong relationship between date_num and violations.
-
-Each property type coefficient represents the deviation in log-odds from the reference category.
-
-For instance, The points representing 'Rooming House' (prprty_RH), 'High Rise' (prprty_HR) and 'Group Home' (prprty_GH), have posterior distribution above 0, suggesting that rooming houses, high-rise buildings and group homes are more likely to have violations than the reference category.
-Narrow credible intervals indicate strong data support.
-
-On the other hand, the point representing 'Nursing Home' (prprty_NH) have posteriors close to 0, suggesting their effects are small or negligible compared to the reference category.
-Narrow credible intervals still indicate strong data support.
-
-The rest of dots representing different levels of 'property type' show various posterior means and credible intervals.
-Most of the points are close to 0 or above 0, providing information about effects of different property types respectively.
+@fig-posteriorvsprior compares the posterior with the prior distribution of the Bayesian model, validating whether the data has a significant impact on the parameter estimates and whether the model is well-fit.
+
+In general, each level shows a narrower posterior distribution than the prior, reflecting that the uncertainty decreases and that the data provides substantial information to update the prior beliefs.
+Parameters with credible intervals far from zero in the posterior are strongly influenced by the data and have meaningful effects, such as the property types of 'Rooming House' (prprty_typRH) and 'Group Home' (prprty_typeGH).
+
+As shown by the point representing the 'Intercept', the posterior credible interval is narrower than the prior, suggesting strong data support for it.
+The negative posterior mean indicates that the baseline log-odds of a violation for the reference property type (when $date_num = 0$) is below 0, implying a low probability of violation.
+
+The posterior point for 'date_num' is very narrow and centered near 0, suggesting that the data indicates little or no effect of inspection duration on the log-odds of a violation.
+The credible interval includes 0, further reinforcing the lack of a strong relationship between 'date_num' and 'violation'.
+
+Additionally, each property type coefficient represents the deviation in log-odds from the reference category, with the posterior distributions reflecting the impact of these property types on the likelihood of violations.
+
+For example, the points representing 'Rooming House' (prprty_RH), 'High Rise' (prprty_HR), and 'Group Home' (prprty_GH), have posterior distribution above 0, suggesting that rooming houses, high-rise buildings and group homes are more likely to have violations than the reference category.
+The narrow credible intervals indicate strong data support for these relationships.
+
+On the other hand, the point representing 'Nursing Home' (prprty_NH) has a posterior close to 0, suggesting that its effect is small or negligible compared to the reference category.
+Despite this, the narrow credible intervals still indicate strong data support for the estimate, confirming the model’s confidence in the result.
+
+The rest of dots representing different levels of 'property type' show varying posterior means and credible intervals.
+Most of the points are either close to 0 or above 0, providing information about effects of different property types on the likelihood of violations respectively.
+These values reflect how each property type deviates from the reference category in terms of log-odds, with the credible intervals offering a measure of uncertainty around the estimates.
 
@@
 
-Trace plot shows samples from all the chains.
-
-In the trance plot, x-axis represents the iteration numbers of the MCMC progress (in this case, up to 4000 iterations per chain), and y-axis displays the sampled values of the posterior distribution for each parameter.
-Each MCMC chain used during sampling is represented by a different color or line style..
-
-If all chains appear to oscillate around the same mean, and overlap significantly, it suggests that the parameter estimates are stable around a consistent mean.
-It is also a good sign if the chains have overlap in most regions and move freely across the posterior distribution.
-There should also be no systematic patterns, trends or large jumps.
+The trace plot shows samples from all the chains.
+
+In the trance plot, the X-axis represents the iteration numbers of the MCMC progress (in this case, up to 4,000 iterations per chain), while the Y-axis displays the sampled values of the posterior distribution for each parameter.
+Each MCMC chain used during sampling is represented by a different color.
+
+If all chains appear to oscillate around the same mean and overlap significantly, it suggests that the parameter estimates are stable around a consistent mean.
+It is also a positive sign if the chains overlap in most regions and move freely across the posterior distribution.
+Additionally, there should be no systematic patterns, trends or large jumps.
 
@@
 
-Moreover, most chains is stabilized and oscillates around a consistent mean.
-The consistent behavior across iterations indciates that the chains have reached stationarity.
-Also, there are no visible divergences or chain-specific trends, suggesting the sampling process is functioning correctly.
-
-In general, the trace plots suggest that MCMC chains are converged, supported by good mixing, stationarity, and consistent sampling across chains, indicating that the posterior estimates for all parameters are likely reliable.
-Slight variability may be adjusted by more iterations, which aimed to gather additional independent samples.
+Moreover, most chains are stabilized and oscillate around a consistent mean.
+This consistent behavior across iterations indicates that the chains have reached stationarity.
+Also, there are no visible divergences or chain-specific trends, suggesting that the sampling process is functioning correctly.
+
+In general, the trace plots suggest that MCMC chains have converged, supported by good mixing, stationarity, and consistent sampling across chains.
+This indicates that the posterior estimates for all parameters are likely reliable.
+If there is any slight variability observed, it could be addressed by additional iterations, which would help gather more independent samples and further stabilize the results.
 
@@
 $\hat{R}$ is a diagnostic measure that compares the variance within each chain to the variance between chains.
-This diagnostic plot is used to asses the convergence of MCMC chains.Ideally, the $\hat{R}$ should be close to 1, so that chains have mixed well and are sampling from the same posterior distribution.
-For $\hat{R} \leq 1.5$, we could say that convergence is acceptable.
+This diagnostic plot is used to asses the convergence of MCMC chains.
+Ideally, the $\hat{R}$ should be close to 1, indicating that the chains have mixed well and are sampling from the same posterior distribution.
+For $\hat{R} \leq 1.5$, we could consider convergence to be acceptable, meaning that the chains are producing reliable parameter estimates.
 
@@
 The plot shows that the R-hat values for all parameters are below 1.05, suggesting that the chains have converged well and are sampling effectively from the posterior distribution.
-The posterior samples are likely reliable for inference, indicating that the results are robust and can be used for interpreting parameter estimates.
+With R-hat values within this range, the posterior samples are likely reliable for inference, indicating that the results could be confidently used for interpreting parameter estimates.
 

### 2024-12-04 paper/paper.qmd
Updated final completed version of paper

@@
 - $\text{logit}(p_i) = \log\left(\frac{p_i}{1 - p_i}\right)$ represents the log-odds of $p_i$.
-- $\beta_0$ is the intercept term of the Bayesian logistic regression, representing the baseline log-odds of a violation when $date = 0$ and 'type' is the reference category.
+- $\beta_0$ is the intercept term of the Bayesian logistic regression, representing the baseline log-odds of a violation when $\text{date} = 0$ and 'type' is the reference category.
 Formula (2) specifies that $\beta_0$ follows normal distribution with a mean of 0 and a variance of $2.5^2$.
@@
 The table firstly lists estimates of coefficients for all parameters.
-The first line suggests an intercept of -6.72 for the model, indicating very low baseline odds of a violation for the reference property type when $date = 0$.
+The first line suggests an intercept of -6.72 for the model, indicating very low baseline odds of a violation for the reference property type when $\text{date} = 0$.
 The second line shows that the estimated coefficient for predictor 'date' is 0.02, which is very small and suggests that the inspection duration has a negligible effect on the violation outcome of observations.

### 2024-12-04 scripts/03-clean_data.R
Updated script for data cleaning

@@ -5,7 +5,7 @@
 # Contact: kylie.gu@mail.utoronto.ca
 # License: MIT
 # Pre-requisites:
-# - The `tidyverse` `dplyr` `lubridate` package must be installed and loaded
+# - The `tidyverse` `dplyr` `lubridate` `arrow` package must be installed and loaded
 # - 02-download_data.R must have been run
 # Any other information needed? Make sure you are in the `Toronto_Fire_Inspection` rproj
 

### 2024-12-04 scripts/03-clean_data.R
Updated script for data cleaning

@@ -5,7 +5,7 @@
 # Contact: kylie.gu@mail.utoronto.ca
 # License: MIT
 # Pre-requisites:
-# - The `tidyverse` `dplyr` `lubridate` `arrow` package must be installed and loaded
+# - The `tidyverse` `dplyr` `lubridate` `janitor` `arrow` package must be installed and loaded
 # - 02-download_data.R must have been run
 # Any other information needed? Make sure you are in the `Toronto_Fire_Inspection` rproj
 
